### 2023-10-10 proposal/proposal.tex
adding proposal and references

\documentclass[12pt]{article}

%% preamble: Keep it clean; only include those you need
\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{enumitem}

% for space filling
\usepackage{lipsum}
% highlighting hyper links
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

%% meta data

\title{Proposal: Bridging Gaps: Investigating COVID-19's Influence on Health Disparities in Connecticut}
\author{Delia Lin\\
  Department of Statistics\\
  University of Connecticut
}

\begin{document}
\maketitle

\paragraph{Introduction}
Social determinants of health (SDOH) are the conditions in which people are born, 
grow, live, work, and age, which significantly influence their overall health and 
well-being. These determinants include factors such as socioeconomic status, education, 
access to healthcare, and the physical environment. Understanding the interactions of 
these elements will be essential for addressing health disparities and developing more 
effective public health policies and interventions.

Current research focuses on how social determinants of health (SDoH) plays a  massive
impact on one's health; it is estimated that 80 percent of a population's health outcomes are 
dictated by SDoH \citep{HOOD2016129}. Often, SDoH, when referring to an individual, can result in racial 
disparities in care when looking at a population\citep{Monroe2023-uq}. It has been shown that major inefficiencies
in the health system are attributed to overlooked prevention opportunities and unequal access
to care.\citep{Allin2014-xn}

\paragraph{Specific Aims}
The question aims to assess the influence of COVID-19 on key social determinants of health 
within various counties and racial groups in Connecticut. While the influence of social factors 
on healthcare access is widely acknowledged, this research question was selected to address the 
pressing need for understanding how the pandemic amplified existing disparities across diverse 
communities. By investigating these factors, we can identify the 
specific ways in which different communities were affected, providing insights for 
targeted interventions, policy-making, and equitable healthcare strategies. 
Current research has shown that in the United States, predominantly black counties experience a 
COVID-19 infection rate that is threefold higher and a mortality rate that is six times higher 
compared to predominantly white counties \citep{Yancy2020-cz}. In addition, during the pandemic, mortality 
rates among historically marginalized minority communities have been 1.9 to 2.4 times higher 
compared to the general population.\citep{Badalov2022-wt}

Research question: What is the extent of COVID-19's impact on social determinants of health factors, including socioeconomic status, housing, transportation, and Medicare access, when comparing the counties and racial groups in Connecticut?

Statistical Questions:
\begin{enumerate}
\item
What is the racial composition within each county?
\item
Is there a correlation between median income and racial identification between the counties?
\item
Is there a correlation between median income and education between the counties?
\item
Is there a difference between transportation accessibility between the counties in Connecticut?
\item
Is there a difference between primary care physician shortage percentages between counties?
\item
Was there an impact on the median household income for any specific racial groups or counties during the year 2020?
\item
Was there a shift in the proportion of the population within different poverty ratios in Connecticut during the year 2020?
\item
Was there a reduction in the percentage of housing units with heating in Connecticut during the year 2020?
\item
Was there a shift in the percentage of Connecticut's population covered by Medicaid or lacking insurance during the year 2020?
\end{enumerate}

\paragraph{Data}
Data was collected from The Agency for Healthcare Research and Quality (AHRQ).
The dataset comprises 64 variables spanning a period of 4 years (2017--2020) 
with observations across the 8 counties in Connecticut. These variables encompass 
a total of 2048 observations. The variables questions include housing, education level, 
income, access to electronic devices, transportation, ESL, and population racial characteristics. 
The dataset includes a range of calculated percentages, median values, and raw observations, 
providing a holistic view of various factors affecting the communities in these counties.

\paragraph{Research Design and Methods}

In this study, descriptive statistics will be utilized to outline the racial composition, 
median incomes, education levels, transportation accessibility, and healthcare indicators 
across different counties and racial groups in Connecticut. Multivariable logistic regression 
will be used to estimate the adjusted odds ratio associations for different SDH factors on 
racial identification over the study period.\citep{Cova2023-yw} Additionally, chi-squared tests will be employed 
to assess significant shifts in population percentages between counties over the span of the 4 years.\citep{Lua2023-tp}

\paragraph{Discussion}
The most challenging part of this investigation would be working with the dataset which 
involves multiple variables and diverse demographics. Managing missing or incomplete data points,
and addressing potential biases in the dataset resulting from surveys are important.

One limitation lies in the availability and quality of data. This dataset does not have any data 
from years after 2020 which may serve to limit potential external validity considerations. There may
also be variability in data collection methods and discrepancies in reporting standards leading to 
missing or incomplete data over the course of 4 years. Another limitation involves the scope of the 
study, focusing on specific counties in Connecticut may not fully capture nationwide disparities. 
Additionally, the research is limited to the factor parameters selected to investigate which  might 
not encompass all relevant social determinants affecting health outcomes.

In the face of unexpected events, I will prioritize transparency. If data limitations arise, efforts 
will be made to clearly document these constraints and their potential impact on the study's conclusions. 
If the impact of COVID is not well represented by the incomplete data in this dataset, I will also look 
into obtaining other existing datasets with observations collected during the study period and after 2020 
to ensure comprehensiveness. Open communication about challenges and potential limitations will be 
maintained to ensure the research's integrity and to provide a foundation for future studies in the field.

Following analysis, I expect to find a greater prevalence of social risk factors within minority populations, 
counties with lower median income will have a greater proportion of minority populations, and social risk 
factors display increasing trends in 2020. These expectations stem from recent reports that have shown that 
minority populations have been disproportionately impacted by the effects of the COVID-19 pandemic. The impact 
of this work lies in informing targeted interventions, policy-making, and resource allocation to alleviate 
current healthcare inequities remnant of the pandemic as well as inform future action. Even if the results 
of this investigation are not what I expected, any conclusions that can be made about socioeconomic factors 
between counties are important for future policies.

This research proposal delves into the impact of COVID-19 on social determinants of health, focusing on 
socioeconomic status, housing, transportation, and Medicare access among Connecticut counties and racial groups. 
Through this research, I hope to be able to enhance the understanding of the connections between social 
determinants and health outcomes specifically in Connecticut, fostering positive changes in healthcare 
systems and advocating for a more equitable society.

\bibliography{../manuscript/ref}
\bibliographystyle{chicago}

\end{document}

### 2023-10-30 manuscript/manuscript.tex
update table

\documentclass[12pt]{article}

%% preamble: Keep it clean; only include those you need
\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
% for space filling
\usepackage{lipsum}
% highlighting hyper links
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

%% meta data

\title{Bridging Gaps: Investigating COVID-19's Influence on Health Disparities in Connecticut}
\author{Delia Lin\\
  Department of Statistics\\
  University of Connecticut
}

\begin{document}
\maketitle

\begin{abstract}
    Social determinants of health (SDOH) are the conditions in which people are born, 
    grow, live, work, and age, which significantly influence their overall health and 
    well-being. These determinants include factors such as socioeconomic status, education, 
    access to healthcare, and the physical environment. Understanding the interactions of 
    these elements will be essential for addressing health disparities and developing more 
    effective public health policies and interventions.  
\end{abstract}

\section{Introduction}\label{sec:intro}

Current research focuses on how social determinants of health (SDoH) plays a  massive
impact on one's health; it is estimated that 80 percent of a population's health outcomes are 
dictated by SDoH \citep{HOOD2016129}. Often, SDoH, when referring to an individual, can result in racial 
disparities in care when looking at a population\citep{Monroe2023-uq}. It has been shown that major inefficiencies
in the health system are attributed to overlooked prevention opportunities and unequal access
to care.\citep{Allin2014-xn}

Understanding the intricate interplay of these social determinants is crucial in addressing health disparities 
and developing effective public health policies and interventions. The COVID-19 pandemic has shed new light on 
these disparities, amplifying existing inequalities within various communities. This research topic gains paramount 
importance in the current context as it seeks to delve into the specific impact of COVID-19 on key social determinants 
of health in different counties and racial groups in Connecticut.

The existing literature underscores the pressing need for research in this area. Studies have shown that predominantly 
black counties in the United States experience significantly higher COVID-19 infection and mortality rates, emphasizing 
the racial disparities prevalent in healthcare outcomes. The pandemic has magnified these discrepancies, leading to 
mortality rates among historically marginalized minority communities that are 1.9 to 2.4 times higher compared to the 
general population \citep{Badalov2022-wt}. Additionally, inefficiencies in the healthcare system have been attributed 
to overlooked prevention opportunities and unequal access to care, necessitating a comprehensive examination 
of these social determinants in the context of the pandemic.

Despite the growing body of research on SDOH, there is a notable gap concerning the specific impact of COVID-19 on 
these determinants within diverse communities. This research aims to bridge this gap by comprehensively assessing how 
the pandemic has influenced key social determinants of health across various counties and racial groups in Connecticut. 
By identifying the specific ways in which different communities were affected, this study contributes valuable insights 
for targeted interventions, policy-making, and the development of equitable healthcare strategies.

% roadmap
The rest of the paper is organized as follows.

The data will be presented in Section\ref{sec:data}

The methods are described in Section\ref{sec:meth}

The results are reported in Section\ref{sec:resu}

A discussion concludes in Section\ref{sec:disc}

\section{Methods}\label{sec:meth}

In this study, descriptive statistics is utilized to outline the total population, racial composition, 
education levels, and average rehospitalization rate across the 8 counties in Connecticut. ANOVA tests were 
conducted to assess the significance of the difference of the variables of median income, poverty level, health insurance, 
utilities access, and electronics access between counties and across the four years (2017, 2018, 2019, 2020). Additional 
Tukey's HSD tests were conducted to determine the specific counties and years that have had significant differences within 
each of the variables for each county.

\section{Data}\label{sec:data}

Data was collected from The Agency for Healthcare Research and Quality (AHRQ).The dataset comprises 7 variables 
spanning a period of 4 years (2017, 2018, 2019, 2020) with observations across the 8 counties in Connecticut. These variables 
encompass a total of 56 observations. The variables questions include housing, education level, income, insurance,
rehospitalization rates, food stamps usage, and population racial characteristics. The dataset includes a range of 
calculated percentages, median values, and raw observations, providing a holistic view of various factors affecting 
the communities in these counties.

\section{Results}\label{sec:resu}

\begin{table}[h]
    \centering
    \caption{Demographics and Education Levels by County} \label{tab:connecticut-counties}
    \begin{tabular}{l|cccccccc}
    \hline
    \textbf{CATEGORY} & \textbf{Fairfield County} & \textbf{Hartford County} & \textbf{Litchfield County} & \textbf{Middlesex County} & \textbf{New Haven County} & \textbf{New London County} & \textbf{Tolland County} & \textbf{Windham County} \\ \hline
    Total Population & 944977 & 894465.25 & 182657.5 & 163318.25 & 858678 & 268477.75 & 151218.75 & 116608.75 \\
    RACE &  &  &  &  &  &  &  &  \\
    American Indian and Alaska Native race alone & 0.24 & 0.3075 & 0.2025 & 0.195 & 0.1725 & 0.605 & 0.05 & 0.565 \\
    Asian & 5.2925 & 5.2925 & 1.9 & 3.0625 & 4.005 & 4.12 & 4.675 & 1.3675 \\
    Black or African American & 11.405 & 13.7025 & 1.83 & 5.385 & 13.34 & 5.8175 & 3.1075 & 2.33 \\
    Native Hawaiian and Pacific Islander & 0.055 & 0.035 & 0 & 0.005 & 0.0225 & 0.025 & 0 & 0.015 \\
    White & 72.6325 & 70.67 & 92.6025 & 88.0875 & 73.2875 & 80.6175 & 88.025 & 88.8725 \\
    Ethnicity &  &  &  &  &  &  &  &  \\
    Hispanic & 19.53 & 17.8275 & 6.15 & 6.12 & 17.885 & 10.5 & 5.4475 & 11.6375 \\
    Average rehospitalization rate in the county &  & 0.1575 & 0.14 & 0.145 & 0.1325 & 0.16 & 0.14 & 0.14 \\
    Education &  &  &  &  &  &  &  &  \\
    Associates & 20.74 & 25 & 27.9225 & 26.46 & 24.4175 & 29.2675 & 26.315 & 30.9775 \\
    Bachelor & 26.53 & 21.4575 & 20.635 & 23.3325 & 18.785 & 18.3175 & 23.4075 & 14.595 \\
    Graduate Degree & 21.14 & 16.475 & 14.6975 & 18.4525 & 16.3425 & 15.18 & 17.865 & 9.55 \\
    HS Graduate & 21.4725 & 26.7175 & 29.5875 & 26.0275 & 30.565 & 29.46 & 27.03 & 33.5125 \\
    Less than High School & 10.12 & 10.3525 & 7.1575 & 5.7275 & 9.8875 & 7.7725 & 5.385 & 11.365 \\ \hline
    \end{tabular}
    \end{table}

Figure\ref{fig:Income by town.pdf} shows the distance against the speed from this dataset.
\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{Income by year.pdf}
  \caption{This is my first figure.}\label{fig:cars}
\end{figure}

\section{Discussion}\label{sec:disc}

What are the main contributions again?

What are the limitations of this study?

What are worth pursuing further in the future?

\appendix

\bibliography{../manuscript/ref}
\bibliographystyle{chicago}

\end{document}

{housing by income.pdf}
{housing by year.pdf}
{Income by town.pdf}
{Inome by year.pdf}
{Rehosp by income/year.pdf}
{Stamps by income/year.pdf}

### 2023-10-30 manuscript/manuscript.tex
add limitations

@@
 
-Figure\ref{fig:Income by town.pdf} shows the distance against the speed from this dataset.
 \begin{figure}[tbp]
@@
   \includegraphics[width=\textwidth]{Income by year.pdf}
-  \caption{This is my first figure.}\label{fig:cars}
+  \caption{Median Income by Year.}\label{fig:cars}
+\end{figure}
+
+\begin{figure}[tbp]
+    \centering
+    \includegraphics[width=\textwidth]{Income by town.pdf}
+    \caption{Median Income by County.}\label{fig:cars}
   \end{figure}
@@
 What are the limitations of this study?
+One limitation lies in the availability and quality of data. This dataset does not have any 
+data from years after 2020 which may serve to limit potential external validity considerations. 
+There may also be variability in data collection methods and discrepancies in reporting standards 
+leading to missing or incomplete data over the course of 4 years. Another limitation involves the scope 
+of the study, focusing on specific counties in Connecticut may not fully capture nationwide disparities. 
+Additionally, the research is limited to the factor parameters selected to investigate which  might not 
+encompass all relevant social determinants affecting health outcomes.
 

### 2023-10-30 manuscript/manuscript.tex
add subsections to discussion

@@
 
-What are the main contributions again?
+The results of the analysis shed light on the intricate relationships between county, race, and key 
+variables such as median income, housing affordability, rehospitalization rates, food stamps usage, 
+uninsured rates, and racial demographics. Understanding these correlations is vital in comprehending 
+the socio-economic and racial disparities prevalent in the studied region.
 
-What are the limitations of this study?
+\subsection{Median Income}
+The disparity in median income across the four years highlights economic fluctuations, with 
+2020 exhibiting the highest income levels. County-wise analysis indicates stark differences, 
+particularly in County 1, which consistently outperforms others. This discrepancy in wealth signifies 
+potential disparities in access to resources and opportunities, which can significantly impact health outcomes.
+
+\subsection{Housing Affordability}
+The stable trend in the percentage of renters spending 50 percent of their income on rent suggests a 
+consistent challenge faced by residents across the years. County 1 and 5 facing significantly higher 
+rates reflect housing affordability issues, possibly indicating economic strains experienced by residents in these areas.
+
+\subsection{Rehospitalization Rates}
+The absence of significant differences in rehospitalization rates by both county and year indicates 
+a consistent healthcare landscape. However, it's crucial to explore the reasons behind this stability to identify 
+potential factors contributing to the overall health system's effectiveness.
+
+\subsection{Food Stamps Usage}
+Counties 8, 2, and 5 having higher percentages of the population on food stamps imply economic challenges 
+faced by residents in these regions. This data aligns with the housing affordability trends, suggesting a potential 
+link between financial struggles and reliance on government assistance programs.
+
+\subsection{Uninsured Rates}
+County 1's consistently high uninsured rate points towards a significant healthcare accessibility issue, 
+possibly linked to economic factors impacting insurance affordability. Year 3's (2019) lower uninsured rate signifies 
+a positive change; understanding the policies or interventions during this period could offer valuable insights into 
+effective healthcare reforms.
+
+\subsection{Racial Disparities}
+The racial demographics highlight disparities in various counties. County 3's higher percentage of white 
+individuals, coupled with County 2, 5, and 1 having the highest black population, points to the need for
+targeted interventions addressing racial health inequalities. These disparities might be indicative of 
+historical, social, and economic factors influencing the healthcare experiences of different racial groups.
+
+\subsection{Limitations}
 One limitation lies in the availability and quality of data. This dataset does not have any 
@@
 
-What are worth pursuing further in the future?
+\subsection{Future Directions}
+These findings underscore the complex interplay between socio-economic status, race, and health outcomes.
+Addressing these disparities requires multifaceted interventions, including economic support, affordable housing initiatives, and targeted healthcare access programs.
+Future research should delve deeper into the root causes of these disparities, considering historical and systemic factors.
+Additionally, policy interventions and community-based programs should be designed to specifically target areas and populations facing the most significant challenges, aiming for a more equitable healthcare landscape for all residents.
 

### 2023-10-30 manuscript/manuscript.tex
add subsubsections into discussion

@@
 
+\ref{tab:connecticut-counties}
+
 \begin{table}[h]
@@
     Hispanic & 19.53 & 17.8275 & 6.15 & 6.12 & 17.885 & 10.5 & 5.4475 & 11.6375 \\
-    Average rehospitalization rate in the county &  & 0.1575 & 0.14 & 0.145 & 0.1325 & 0.16 & 0.14 & 0.14 \\
     Education &  &  &  &  &  &  &  &  \\
@@
 
-\subsection{Median Income}
+There does not appear to be a significant relationship produced over the span of four years between the variables for housing affordability
+
+\subsubsection{Median Income}
 The disparity in median income across the four years highlights economic fluctuations, with 
-2020 exhibiting the highest income levels. County-wise analysis indicates stark differences, 
-particularly in County 1, which consistently outperforms others. This discrepancy in wealth signifies 
-potential disparities in access to resources and opportunities, which can significantly impact health outcomes.
+2020 exhibiting the highest income levels. County-wise analysis reveals that county 1 has a significantly 
+greater median income than other counties. This discrepancy in wealth signifies potential disparities in 
+access to resources and opportunities, which can significantly impact health outcomes.
 
-\subsection{Housing Affordability}
+\subsubsection{Housing Affordability}
 The stable trend in the percentage of renters spending 50 percent of their income on rent suggests a 
@@
 
-\subsection{Rehospitalization Rates}
+\subsubsection{Rehospitalization Rates}
 The absence of significant differences in rehospitalization rates by both county and year indicates 
@@
 
-\subsection{Food Stamps Usage}
+\subsubsection{Food Stamps Usage}
 Counties 8, 2, and 5 having higher percentages of the population on food stamps imply economic challenges 
@@
 
-\subsection{Uninsured Rates}
+\subsubsection{Uninsured Rates}
 County 1's consistently high uninsured rate points towards a significant healthcare accessibility issue, 
@@
 
-\subsection{Racial Disparities}
+\subsubsection{Racial Disparities}
 The racial demographics highlight disparities in various counties. County 3's higher percentage of white 
@@
 These findings underscore the complex interplay between socio-economic status, race, and health outcomes. 
-Addressing these disparities requires multifaceted interventions, including economic support, affordable housing initiatives, and targeted healthcare access programs.
-Future research should delve deeper into the root causes of these disparities, considering historical and systemic factors.
-Additionally, policy interventions and community-based programs should be designed to specifically target areas and populations facing the most significant challenges, aiming for a more equitable healthcare landscape for all residents.
+Addressing these disparities requires multifaceted interventions, including economic support, affordable 
+housing initiatives, and targeted healthcare access programs. Future research should delve deeper into the 
+root causes of these disparities, considering historical and systemic factors. Additionally, policy interventions 
+and community-based programs should be designed to specifically target areas and populations facing the most 
+significant challenges, aiming for a more equitable healthcare landscape for all residents.
 

### 2023-10-31 manuscript/manuscript.tex
update table format

@@
 \usepackage[colorlinks=true, citecolor=blue]{hyperref}
+\usepackage{tabularx}
+\usepackage{adjustbox}
 
@@
 
-\ref{tab:connecticut-counties}
-
-\begin{table}[h]
-    \centering
-    \caption{Demographics and Education Levels by County} \label{tab:connecticut-counties}
-    \begin{tabular}{l|cccccccc}
-    \hline
-    \textbf{CATEGORY} & \textbf{Fairfield County} & \textbf{Hartford County} & \textbf{Litchfield County} & \textbf{Middlesex County} & \textbf{New Haven County} & \textbf{New London County} & \textbf{Tolland County} & \textbf{Windham County} \\ \hline
-    Total Population & 944977 & 894465.25 & 182657.5 & 163318.25 & 858678 & 268477.75 & 151218.75 & 116608.75 \\
-    RACE &  &  &  &  &  &  &  &  \\
-    American Indian and Alaska Native race alone & 0.24 & 0.3075 & 0.2025 & 0.195 & 0.1725 & 0.605 & 0.05 & 0.565 \\
-    Asian & 5.2925 & 5.2925 & 1.9 & 3.0625 & 4.005 & 4.12 & 4.675 & 1.3675 \\
-    Black or African American & 11.405 & 13.7025 & 1.83 & 5.385 & 13.34 & 5.8175 & 3.1075 & 2.33 \\
-    Native Hawaiian and Pacific Islander & 0.055 & 0.035 & 0 & 0.005 & 0.0225 & 0.025 & 0 & 0.015 \\
-    White & 72.6325 & 70.67 & 92.6025 & 88.0875 & 73.2875 & 80.6175 & 88.025 & 88.8725 \\
-    Ethnicity &  &  &  &  &  &  &  &  \\
-    Hispanic & 19.53 & 17.8275 & 6.15 & 6.12 & 17.885 & 10.5 & 5.4475 & 11.6375 \\
-    Education &  &  &  &  &  &  &  &  \\
-    Associates & 20.74 & 25 & 27.9225 & 26.46 & 24.4175 & 29.2675 & 26.315 & 30.9775 \\
-    Bachelor & 26.53 & 21.4575 & 20.635 & 23.3325 & 18.785 & 18.3175 & 23.4075 & 14.595 \\
-    Graduate Degree & 21.14 & 16.475 & 14.6975 & 18.4525 & 16.3425 & 15.18 & 17.865 & 9.55 \\
-    HS Graduate & 21.4725 & 26.7175 & 29.5875 & 26.0275 & 30.565 & 29.46 & 27.03 & 33.5125 \\
-    Less than High School & 10.12 & 10.3525 & 7.1575 & 5.7275 & 9.8875 & 7.7725 & 5.385 & 11.365 \\ \hline
-    \end{tabular}
+\begin{table}[]
+  \resizebox{\columnwidth}{!}{%
+  \begin{tabular}{lllllllllllllll}
+                            &                                              &                  &                 &                   &                  &                  &                   &                &                &  &  &  &  &  \\
+  \textbf{County}           &                                              & Fairfield County & Hartford County & Litchfield County & Middlesex County & New Haven County & New London County & Tolland County & Windham County &  &  &  &  &  \\
+  \textbf{Total Population} &                                              & 944977           & 894465.25       & 182657.5          & 163318.25        & 858678           & 268477.75         & 151218.75      & 116608.75      &  &  &  &  &  \\
+  \textbf{Race}             & American Indian and Alaska Native race alone & 0.24             & 0.3075          & 0.2025            & 0.195            & 0.1725           & 0.605             & 0.05           & 0.565          &  &  &  &  &  \\
+                            & Asian                                        & 5.2925           & 5.2925          & 1.9               & 3.0625           & 4.005            & 4.12              & 4.675          & 1.3675         &  &  &  &  &  \\
+                            & Black or African American                    & 11.405           & 13.7025         & 1.83              & 5.385            & 13.34            & 5.8175            & 3.1075         & 2.33           &  &  &  &  &  \\
+                            & Native Hawaiian and Pacific Islander         & 0.055            & 0.035           & 0                 & 0.005            & 0.0225           & 0.025             & 0              & 0.015          &  &  &  &  &  \\
+                            & White                                        & 72.6325          & 70.67           & 92.6025           & 88.0875          & 73.2875          & 80.6175           & 88.025         & 88.8725        &  &  &  &  &  \\
+  \textbf{Ethnicity}        & Hispanic                                     & 19.53            & 17.8275         & 6.15              & 6.12             & 17.885           & 10.5              & 5.4475         & 11.6375        &  &  &  &  &  \\
+  \textbf{Education}        & Associates                                   & 20.74            & 25              & 27.9225           & 26.46            & 24.4175          & 29.2675           & 26.315         & 30.9775        &  &  &  &  &  \\
+                            & Bachelor                                     & 26.53            & 21.4575         & 20.635            & 23.3325          & 18.785           & 18.3175           & 23.4075        & 14.595         &  &  &  &  &  \\
+                            & Graduate Degree                              & 21.14            & 16.475          & 14.6975           & 18.4525          & 16.3425          & 15.18             & 17.865         & 9.55           &  &  &  &  &  \\
+                            & HS Graduate                                  & 21.4725          & 26.7175         & 29.5875           & 26.0275          & 30.565           & 29.46             & 27.03          & 33.5125        &  &  &  &  &  \\
+                            & Less the High School                         & 10.12            & 10.3525         & 7.1575            & 5.7275           & 9.8875           & 7.7725            & 5.385          & 11.365         &  &  &  &  &  \\
+                            &                                              &                  &                 &                   &                  &                  &                   &                &                &  &  &  &  &
+  \end{tabular}%
+  }
   \end{table}
@@
 
-\subsubsection{Median Income}
+\subsection{Median Income}
 The disparity in median income across the four years highlights economic fluctuations, with 
@@
 greater median income than other counties. This discrepancy in wealth signifies potential disparities in 
-access to resources and opportunities, which can significantly impact health outcomes.
-
-\subsubsection{Housing Affordability}
-The stable trend in the percentage of renters spending 50 percent of their income on rent suggests a 
+access to resources and opportunities, which can significantly impact health outcomes. The stable trend 
+in the percentage of renters spending 50 percent of their income on rent suggests a 
 consistent challenge faced by residents across the years. County 1 and 5 facing significantly higher 
 rates reflect housing affordability issues, possibly indicating economic strains experienced by residents in these areas.
-
-\subsubsection{Rehospitalization Rates}
 The absence of significant differences in rehospitalization rates by both county and year indicates 
-a consistent healthcare landscape. However, it's crucial to explore the reasons behind this stability to identify 
-potential factors contributing to the overall health system's effectiveness.
-
-\subsubsection{Food Stamps Usage}
+a consistent healthcare landscape over the years prior to the 2020 pandemic.
 Counties 8, 2, and 5 having higher percentages of the population on food stamps imply economic challenges 
@@
 link between financial struggles and reliance on government assistance programs.
-
-\subsubsection{Uninsured Rates}
-County 1's consistently high uninsured rate points towards a significant healthcare accessibility issue, 
+County 1's significant high uninsured rate points towards a significant healthcare accessibility issue, 
 possibly linked to economic factors impacting insurance affordability. Year 3's (2019) lower uninsured rate signifies 

### 2023-10-31 manuscript/manuscript.tex
removing subsections in discussion

@@
 
-There does not appear to be a significant relationship produced over the span of four years between the variables for housing affordability
+The disparity in median income over the studied years, particularly the peak observed in 2020, 
+signifies economic fluctuations. Notably, county 1 stands out with significantly higher income 
+compared to other counties, indicating potential disparities in resource access and opportunities. 
+This wealth gap implies potential repercussions on community health outcomes. The consistent trend in 
+the percentage of income spent on rent underscores a persistent challenge for residents, especially 
+noticeable in counties 1 and 5, indicating enduring economic pressure.
 
-\subsection{Median Income}
-The disparity in median income across the four years highlights economic fluctuations, with 
-2020 exhibiting the highest income levels. County-wise analysis reveals that county 1 has a significantly 
-greater median income than other counties. This discrepancy in wealth signifies potential disparities in 
-access to resources and opportunities, which can significantly impact health outcomes. The stable trend 
-in the percentage of renters spending 50 percent of their income on rent suggests a 
-consistent challenge faced by residents across the years. County 1 and 5 facing significantly higher 
-rates reflect housing affordability issues, possibly indicating economic strains experienced by residents in these areas.
-The absence of significant differences in rehospitalization rates by both county and year indicates 
-a consistent healthcare landscape over the years prior to the 2020 pandemic.
-Counties 8, 2, and 5 having higher percentages of the population on food stamps imply economic challenges 
-faced by residents in these regions. This data aligns with the housing affordability trends, suggesting a potential 
-link between financial struggles and reliance on government assistance programs.
-County 1's significant high uninsured rate points towards a significant healthcare accessibility issue, 
-possibly linked to economic factors impacting insurance affordability. Year 3's (2019) lower uninsured rate signifies 
-a positive change; understanding the policies or interventions during this period could offer valuable insights into 
-effective healthcare reforms.
+Rehospitalization rates demonstrate stability across counties and years leading up to 2020, suggesting 
+a consistent healthcare landscape. Counties 8, 2, and 5 exhibiting higher food stamp usage point to economic 
+challenges faced by residents in these regions. This trend aligns with housing affordability issues, 
+indicating a correlation between financial stress and reliance on government assistance programs.
+
+The notably high uninsured rate in county 1 raises concerns about healthcare accessibility, likely 
+linked to economic factors impacting insurance affordability. Conversely, the lower uninsured rate in 
+Year 3 (2019) signifies positive progress. Analyzing the policies or interventions implemented during 
+this period could provide valuable insights for effective healthcare reforms, offering potential guidance 
+for future initiatives.
 

### 2023-10-31 manuscript/manuscript.tex
add demographic descriptions
add new income graph
removing two graphs

@@
 
+\section{Data}\label{sec:data}
+
+Data was collected from The Agency for Healthcare Research and Quality (AHRQ).The dataset comprises 7 variables 
+spanning a period of 4 years (2017, 2018, 2019, 2020) with observations across the 8 counties in Connecticut. These variables 
+encompass a total of 56 observations. The variables questions include housing, education level, income, insurance,
+rehospitalization rates, food stamps usage, and population racial characteristics. The dataset includes a range of 
+calculated percentages, median values, and raw observations, providing a holistic view of various factors affecting 
+the communities in these counties.
+
 \section{Methods}\label{sec:meth}
@@
 
-\section{Data}\label{sec:data}
-
-Data was collected from The Agency for Healthcare Research and Quality (AHRQ).The dataset comprises 7 variables 
-spanning a period of 4 years (2017, 2018, 2019, 2020) with observations across the 8 counties in Connecticut. These variables 
-encompass a total of 56 observations. The variables questions include housing, education level, income, insurance,
-rehospitalization rates, food stamps usage, and population racial characteristics. The dataset includes a range of 
-calculated percentages, median values, and raw observations, providing a holistic view of various factors affecting 
-the communities in these counties.
-
 \section{Results}\label{sec:resu}
 
+\ref{tab:Demographics}
+\ref{fig:Income by County Graph}
+
 \begin{table}[]
+  \label{tab:Demographics}
+  \caption{Demographics and Education Levels.}
   \resizebox{\columnwidth}{!}{%
@@
   \textbf{Total Population} &                                              & 944977           & 894465.25       & 182657.5          & 163318.25        & 858678           & 268477.75         & 151218.75      & 116608.75      &  &  &  &  &  \\
-  \textbf{Race}             & American Indian and Alaska Native race alone & 0.24             & 0.3075          & 0.2025            & 0.195            & 0.1725           & 0.605             & 0.05           & 0.565          &  &  &  &  &  \\
+  \textbf{Race (Percent)}             & American Indian and Alaska Native race alone & 0.24             & 0.3075          & 0.2025            & 0.195            & 0.1725           & 0.605             & 0.05           & 0.565          &  &  &  &  &  \\
                             & Asian                                        & 5.2925           & 5.2925          & 1.9               & 3.0625           & 4.005            & 4.12              & 4.675          & 1.3675         &  &  &  &  &  \\
@@
                             & White                                        & 72.6325          & 70.67           & 92.6025           & 88.0875          & 73.2875          & 80.6175           & 88.025         & 88.8725        &  &  &  &  &  \\
-  \textbf{Ethnicity}        & Hispanic                                     & 19.53            & 17.8275         & 6.15              & 6.12             & 17.885           & 10.5              & 5.4475         & 11.6375        &  &  &  &  &  \\
-  \textbf{Education}        & Associates                                   & 20.74            & 25              & 27.9225           & 26.46            & 24.4175          & 29.2675           & 26.315         & 30.9775        &  &  &  &  &  \\
+  \textbf{Ethnicity (Percent)}        & Hispanic                                     & 19.53            & 17.8275         & 6.15              & 6.12             & 17.885           & 10.5              & 5.4475         & 11.6375        &  &  &  &  &  \\
+  \textbf{Education (Percent)}        & Associates                                   & 20.74            & 25              & 27.9225           & 26.46            & 24.4175          & 29.2675           & 26.315         & 30.9775        &  &  &  &  &  \\
                             & Bachelor                                     & 26.53            & 21.4575         & 20.635            & 23.3325          & 18.785           & 18.3175           & 23.4075        & 14.595         &  &  &  &  &  \\
@@
   \begin{figure}[tbp]
+    \label{fig:Income by County Graph}
     \centering
-  \includegraphics[width=\textwidth]{Income by year.pdf}
-  \caption{Median Income by Year.}\label{fig:cars}
-\end{figure}
-
-\begin{figure}[tbp]
-    \centering
-    \includegraphics[width=\textwidth]{Income by town.pdf}
-    \caption{Median Income by County.}\label{fig:cars}
+    \includegraphics[width=\textwidth]{Income by County Graph.pdf}
+    \caption{Median Income by County.}
   \end{figure}
@@
 
-\subsubsection{Racial Disparities}
 The racial demographics highlight disparities in various counties. County 3's higher percentage of white 

### 2023-11-13 manuscript/manuscript.tex
fix spelling and edit wording of abstract

@@
 \begin{abstract}
-    Social determinants of health (SDOH) are the conditions in which people are born, 
-    grow, live, work, and age, which significantly influence their overall health and 
-    well-being. These determinants include factors such as socioeconomic status, education, 
-    access to healthcare, and the physical environment. Understanding the interactions of 
-    these elements will be essential for addressing health disparities and developing more 
-    effective public health policies and interventions.  
+  Social determinants of health (SDoH) are the conditions in which people are born, 
+  grow, live, work, and age, significantly influencing their overall health and well-being. 
+  These determinants include socioeconomic status, education, access to healthcare, and the 
+  physical environment. Understanding the interactions of these elements will be essential for 
+  addressing health disparities and developing more effective public health policies and interventions.
 \end{abstract}

### 2023-11-13 manuscript/manuscript.tex
consistent SDoH acronym + removed repetitive years

@@
 
-Despite the growing body of research on SDOH, there is a notable gap concerning the specific impact of COVID-19 on 
+Despite the growing body of research on SDoH, there is a notable gap concerning the specific impact of COVID-19 on 
 these determinants within diverse communities. This research aims to bridge this gap by comprehensively assessing how 
@@
 conducted to assess the significance of the difference of the variables of median income, poverty level, health insurance, 
-utilities access, and electronics access between counties and across the four years (2017, 2018, 2019, 2020). Additional 
+utilities access, and electronics access between counties and across the four years. Additional 
 Tukey's HSD tests were conducted to determine the specific counties and years that have had significant differences within 

### 2023-11-13 manuscript/manuscript.tex
added specific counties in methods

@@
 Data was collected from The Agency for Healthcare Research and Quality (AHRQ).The dataset comprises 7 variables 
-spanning a period of 4 years (2017, 2018, 2019, 2020) with observations across the 8 counties in Connecticut. These variables 
+spanning a period of 4 years (2017, 2018, 2019, 2020) with observations across the 8 counties(Fairfield County, Hartford County, Litchfield County, Middlesex County, New Haven County, New London County, Tolland County, Windham County) in Connecticut.
+These variables
 encompass a total of 56 observations. The variables questions include housing, education level, income, insurance,

### 2023-12-15 manuscript/manuscript.tex
remove income and housing graphs

@@
 \usepackage{adjustbox}
+
+% double spacing
+\usepackage{setspace}
+\doublespacing
 
@@
 
-The data will be presented in Section\ref{sec:data}
+- The data will be presented in Section \ref{sec:data}
 
-The methods are described in Section\ref{sec:meth}
+- The methods are described in Section \ref{sec:meth}
 
-The results are reported in Section\ref{sec:resu}
+- The results are reported in Section \ref{sec:resu}
 
-A discussion concludes in Section\ref{sec:disc}
+- A discussion concludes in Section \ref{sec:disc}
 
@@
 Data was collected from The Agency for Healthcare Research and Quality (AHRQ).The dataset comprises 7 variables 
-spanning a period of 4 years (2017, 2018, 2019, 2020) with observations across the 8 counties(Fairfield County, Hartford County, Litchfield County, Middlesex County, New Haven County, New London County, Tolland County, Windham County) in Connecticut.
-These variables
+spanning a period of 4 years (2017, 2018, 2019, 2020) with observations across the 8 counties(Fairfield County, Hartford County, 
+Litchfield County, Middlesex County, New Haven County, New London County, Tolland County, Windham County) in Connecticut. These variables 
 encompass a total of 56 observations. The variables questions include housing, education level, income, insurance,
@@
 In this study, descriptive statistics is utilized to outline the total population, racial composition, 
-education levels, and average rehospitalization rate across the 8 counties in Connecticut. ANOVA tests were 
+education levels, and average rehospitalization rate across the 8 counties in Connecticut. Chi-squared analyses were 
 conducted to assess the significance of the difference of the variables of median income, poverty level, health insurance, 
@@
 
-\begin{table}[]
+\begin{table}[h]
 \label{tab:Demographics}
-  \caption{Demographics and Education Levels.}
+  \caption{Demographics and Education Levels for Counties 1-4}
   \resizebox{\columnwidth}{!}{%
-  \begin{tabular}{lllllllllllllll}
-                            &                                              &                  &                 &                   &                  &                  &                   &                &                &  &  &  &  &  \\
-  \textbf{County}           &                                              & Fairfield County & Hartford County & Litchfield County & Middlesex County & New Haven County & New London County & Tolland County & Windham County &  &  &  &  &  \\
-  \textbf{Total Population} &                                              & 944977           & 894465.25       & 182657.5          & 163318.25        & 858678           & 268477.75         & 151218.75      & 116608.75      &  &  &  &  &  \\
-  \textbf{Race (Percent)}             & American Indian and Alaska Native race alone & 0.24             & 0.3075          & 0.2025            & 0.195            & 0.1725           & 0.605             & 0.05           & 0.565          &  &  &  &  &  \\
-                            & Asian                                        & 5.2925           & 5.2925          & 1.9               & 3.0625           & 4.005            & 4.12              & 4.675          & 1.3675         &  &  &  &  &  \\
-                            & Black or African American                    & 11.405           & 13.7025         & 1.83              & 5.385            & 13.34            & 5.8175            & 3.1075         & 2.33           &  &  &  &  &  \\
-                            & Native Hawaiian and Pacific Islander         & 0.055            & 0.035           & 0                 & 0.005            & 0.0225           & 0.025             & 0              & 0.015          &  &  &  &  &  \\
-                            & White                                        & 72.6325          & 70.67           & 92.6025           & 88.0875          & 73.2875          & 80.6175           & 88.025         & 88.8725        &  &  &  &  &  \\
-  \textbf{Ethnicity (Percent)}        & Hispanic                                     & 19.53            & 17.8275         & 6.15              & 6.12             & 17.885           & 10.5              & 5.4475         & 11.6375        &  &  &  &  &  \\
-  \textbf{Education (Percent)}        & Associates                                   & 20.74            & 25              & 27.9225           & 26.46            & 24.4175          & 29.2675           & 26.315         & 30.9775        &  &  &  &  &  \\
-                            & Bachelor                                     & 26.53            & 21.4575         & 20.635            & 23.3325          & 18.785           & 18.3175           & 23.4075        & 14.595         &  &  &  &  &  \\
-                            & Graduate Degree                              & 21.14            & 16.475          & 14.6975           & 18.4525          & 16.3425          & 15.18             & 17.865         & 9.55           &  &  &  &  &  \\
-                            & HS Graduate                                  & 21.4725          & 26.7175         & 29.5875           & 26.0275          & 30.565           & 29.46             & 27.03          & 33.5125        &  &  &  &  &  \\
-                            & Less the High School                         & 10.12            & 10.3525         & 7.1575            & 5.7275           & 9.8875           & 7.7725            & 5.385          & 11.365         &  &  &  &  &  \\
-                            &                                              &                  &                 &                   &                  &                  &                   &                &                &  &  &  &  &
+  \begin{tabular}{lccccc}
+    \toprule
+    \textbf{Category} & \textbf{Fairfield County} & \textbf{Hartford County} & \textbf{Litchfield County} & \textbf{Middlesex County} \\
+    \midrule
+    Total Population & 944,977 & 894,465.25 & 182,657.5 & 163,318.25 \\
+    Race (Percent) & & & & \\
+    \quad American Indian and Alaska Native & 0.24 & 0.3075 & 0.2025 & 0.195 \\
+    \quad Asian & 5.2925 & 5.2925 & 1.9 & 3.0625 \\
+    \quad Black or African American & 11.405 & 13.7025 & 1.83 & 5.385 \\
+    \quad Native Hawaiian and Pacific Islander & 0.055 & 0.035 & 0 & 0.005 \\
+    \quad White & 72.6325 & 70.67 & 92.6025 & 88.0875 \\
+    Ethnicity (Percent) & & & & \\
+    \quad Hispanic & 19.53 & 17.8275 & 6.15 & 6.12 \\
+    Education (Percent) & & & & \\
+    \quad Associates & 20.74 & 25 & 27.9225 & 26.46 \\
+    \quad Bachelor & 26.53 & 21.4575 & 20.635 & 23.3325 \\
+    \quad Graduate Degree & 21.14 & 16.475 & 14.6975 & 18.4525 \\
+    \quad HS Graduate & 21.4725 & 26.7175 & 29.5875 & 26.0275 \\
+    \quad Less than High School & 10.12 & 10.3525 & 7.1575 & 5.7275 \\
+    \bottomrule
+  \end{tabular}%
+  }
+\end{table}
+
+\begin{table}[h]
+  \label{tab:Demographics}
+  \caption{Demographics and Education Levels for Counties 5-8}
+  \resizebox{\columnwidth}{!}{%
+  \begin{tabular}{lcccc}
+    \toprule
+    \textbf{Category} & \textbf{New Haven County} & \textbf{New London County} & \textbf{Tolland County} & \textbf{Windham County} \\
+    \midrule
+    Total Population & 858,678 & 268,477.75 & 151,218.75 & 116,608.75 \\
+    Race (Percent) & & & & \\
+    \quad American Indian and Alaska Native & 0.1725 & 0.605 & 0.05 & 0.565 \\
+    \quad Asian & 4.005 & 4.12 & 4.675 & 1.3675 \\
+    \quad Black or African American & 13.34 & 5.8175 & 3.1075 & 2.33 \\
+    \quad Native Hawaiian and Pacific Islander & 0.0225 & 0.025 & 0 & 0.015 \\
+    \quad White & 73.2875 & 80.6175 & 88.025 & 88.8725 \\
+    Ethnicity (Percent) & & & & \\
+    \quad Hispanic & 17.885 & 10.5 & 5.4475 & 11.6375 \\
+    Education (Percent) & & & & \\
+    \quad Associates & 24.4175 & 29.2675 & 26.315 & 30.9775 \\
+    \quad Bachelor & 18.785 & 18.3175 & 23.4075 & 14.595 \\
+    \quad Graduate Degree & 16.3425 & 15.18 & 17.865 & 9.55 \\
+    \quad HS Graduate & 30.565 & 29.46 & 27.03 & 33.5125 \\
+    \quad Less than High School & 9.8875 & 7.7725 & 5.385 & 11.365 \\
+    \bottomrule
   \end{tabular}%
@@
   \end{figure}
+
+\begin{table}[htbp]
+  \centering
+  \resizebox{\columnwidth}{!}{%
+  \begin{tabular}{lllrrrr}
+  \toprule
+  & & & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{2}{l}{95\% Confidence} \\
+  County 1(I) & County 2(J) & Mean Difference(I-J) & \multicolumn{1}{l}{Std. Error} & \multicolumn{1}{l}{Sig.} & \multicolumn{1}{l}{Lower Bound} & \multicolumn{1}{l}{Upper Bound} \\
+  \midrule
+  Fairfield County & Hartford County & 20565.50000* & 1883.47243 & \textbf{<.001} & 14327.6034 & 26803.3966 \\
+  & Litchfield County & 14919.50000* & 1883.47243 & \textbf{<.001} & 8681.6034 & 21157.3966 \\
+  & Middlesex County & 9671.75000* & 1883.47243 & \textbf{<.001} & 3433.8534 & 15909.6466 \\
+  & New Haven County & 25662.75000* & 1883.47243 & \textbf{<.001} & 19424.8534 & 31900.6466 \\
+  & New London County & 21456.50000* & 1883.47243 & \textbf{<.001} & 15218.6034 & 27694.3966 \\
+  & Tolland County & 8705.00000* & 1883.47243 & \textbf{0.002} & 2467.1034 & 14942.8966 \\
+  & Windham County & 28671.00000* & 1883.47243 & \textbf{<.001} & 22433.1034 & 34908.8966 \\
+  \midrule
+  Hartford County & Fairfield County & -20565.50* & 1883.47 & \textbf{<.001} & -26803.40 & -14327.60 \\
+  & Litchfield County & -5646 & 1883.47 & 0.096 & -11883.90 & 591.90 \\
+  & Middlesex County & -10893.75* & 1883.47 & \textbf{<.001} & -17131.65 & -4655.85 \\
+  & New Haven County & 5097.25 & 1883.47 & 0.169 & -1140.65 & 11335.15 \\
+  & New London County & 891 & 1883.47 & 1 & -5346.90 & 7128.90 \\
+  & Tolland County & -11860.50* & 1883.47 & \textbf{<.001} & -18098.40 & -5622.60 \\
+  & Windham County & 8105.50* & 1883.47 & 0.005 & 1867.60 & 14343.40 \\
+  \midrule
+  Litchfield County & Fairfield County & -14919.50* & 1883.47 & \textbf{<.001} & -21157.40 & -8681.60 \\
+  & Hartford County & 5646 & 1883.47 & 0.096 & -591.90 & 11883.90 \\
+  & Middlesex County & -5247.75 & 1883.47 & 0.145 & -11485.65 & 990.15 \\
+  & New Haven County & 10743.25* & 1883.47 & \textbf{<.001} & 4505.35 & 16981.15 \\
+  & New London County & 6537 & 1883.47 & 0.035 & 299.10 & 12774.90 \\
+  & Tolland County & -6214.5 & 1883.47 & 0.051 & -12452.40 & 23.40 \\
+  & Windham County & 13751.50* & 1883.47 & \textbf{<.001}  & 7513.60 & 19989.40 \\
+  \midrule
+  Middlesex County & Fairfield County & -9671.75* &  & 1883.47 & <.001 & -15909.65 & -3433.85 \\
+  & Hartford County & 10893.75* & 1883.47 & <.001 & 4655.85 & 17131.65 \\
+  & Litchfield County & 5247.75 & 1883.47 & 0.145 & -990.15 & 11485.65 \\
+  & New Haven County & 15991.00* & 1883.47 & <.001 & 9753.10 & 22228.90 \\
+  & New London County & 11784.75* & 1883.47 & <.001 & 5546.85 & 18022.65 \\
+  & Tolland County & -966.75 & 1883.47 & 0.999 & -7204.65 & 5271.15 \\
+  & Windham County & 18999.25* & 1883.47 & <.001 & 12761.35 & 25237.15 \\
+  \midrule
+  New Haven County & Fairfield County & -25662.75* &  & 1883.47 & <.001 & -31900.65 & -19424.85 \\
+  & Hartford County & -5097.25 & 1883.47 & 0.169 & -11335.15 & 1140.65 \\
+  & Litchfield County & -10743.25* & 1883.47 & <.001 & -16981.15 & -4505.35 \\
+  & Middlesex County & -15991.00* & 1883.47 & <.001 & -22228.90 & -9753.10 \\
+  & New London County & -4206.25 & 1883.47 & 0.368 & -10444.15 & 2031.65 \\
+  & Tolland County & -16957.75* & 1883.47 & <.001 & -23195.65 & -10719.85 \\
+  & Windham County & 3008.25 & 1883.47 & 0.747 & -3229.65 & 9246
+  \midrule
+  New London County & Fairfield County & -21456.50* & 1883.47 & <.001 & -27694.40 & -15218.60 \\
+  & Hartford County & -891 & 1883.47 & 1 & -7128.90 & 5346.90 \\
+  & Litchfield County & -6537.00* & 1883.47 & 0.035 & -12774.90 & -299.10 \\
+  & Middlesex County & -11784.75* & 1883.47 & <.001 & -18022.65 & -5546.85 \\
+  & New Haven County & 4206.25 & 1883.47 & 0.368 & -2031.65 & 10444.15 \\
+  & Tolland County & -12751.50* & 1883.47 & <.001 & -18989.40 & -6513.60 \\
+  & Windham County & 7214.50* & 1883.47 & 0.016 & 976.60 & 13452.40 \\
+  \midrule
+  Tolland County & Fairfield County & -8705.00* & 1883.47 & 0.002 & -14942.90 & -2467.10 \\
+  & Hartford County & 11860.50* & 1883.47 & <.001 & 5622.60 & 18098.40 \\
+  & Litchfield County & 6214.50 & 1883.47 & 0.051 & -23.40 & 12452.40 \\
+  & Middlesex County & 966.75 & 1883.47 & 0.999 & -5271.15 & 7204.65 \\
+  & New Haven County & 16957.75* & 1883.47 & <.001 & 10719.85 & 23195.65 \\
+  & New London County & 12751.50* & 1883.47 & <.001 & 6513.60 & 18989.40 \\
+  & Windham County & 19966.00* & 1883.47 & <.001 & 13728.10 & 26203.90 \\
+  \midrule
+  Windham County & Fairfield County & -28671.00* &  & 1883.47 & <.001 & -34908.90 & -22433.10 \\
+  & Hartford County & -8105.50* & 1883.47 & 0.005 & -14343.40 & -1867.60 \\
+  & Litchfield County & -13751.50* & 1883.47 & <.001 & -19989.40 & -7513.60 \\
+  & Middlesex County & -18999.25* & 1883.47 & <.001 & -25237.15 & -12761.35 \\
+  & New Haven County & -3008.25 & 1883.47 & 0.747 & -9246.15 & 3229.65 \\
+  & New London County & -7214.50* & 1883.47 & 0.016 & -13452.40 & -976.60 \\
+  & Tolland County & -19966.00* & 1883.47 & <.001 & -26203.90 & -13728.10 \\
+  \end{tabular}%
+  }
+\end{table}
 

### 2023-12-15 manuscript/manuscript.tex
Add education and income by county graphs

--- 2023-11-13 manuscript/manuscript.tex
@@
 
-\begin{table}[]
+\begin{table}[h]
 \label{tab:Demographics}
-  \caption{Demographics and Education Levels.}
+  \caption{Demographics and Education Levels for Counties 1-4}
   \resizebox{\columnwidth}{!}{%
-  \begin{tabular}{lllllllllllllll}
-                            &                                              &                  &                 &                   &                  &                  &                   &                &                &  &  &  &  &  \\
-  \textbf{County}           &                                              & Fairfield County & Hartford County & Litchfield County & Middlesex County & New Haven County & New London County & Tolland County & Windham County &  &  &  &  &  \\
-  \textbf{Total Population} &                                              & 944977           & 894465.25       & 182657.5          & 163318.25        & 858678           & 268477.75         & 151218.75      & 116608.75      &  &  &  &  &  \\
-  \textbf{Race (Percent)}             & American Indian and Alaska Native race alone & 0.24             & 0.3075          & 0.2025            & 0.195            & 0.1725           & 0.605             & 0.05           & 0.565          &  &  &  &  &  \\
-                            & Asian                                        & 5.2925           & 5.2925          & 1.9               & 3.0625           & 4.005            & 4.12              & 4.675          & 1.3675         &  &  &  &  &  \\
-                            & Black or African American                    & 11.405           & 13.7025         & 1.83              & 5.385            & 13.34            & 5.8175            & 3.1075         & 2.33           &  &  &  &  &  \\
-                            & Native Hawaiian and Pacific Islander         & 0.055            & 0.035           & 0                 & 0.005            & 0.0225           & 0.025             & 0              & 0.015          &  &  &  &  &  \\
-                            & White                                        & 72.6325          & 70.67           & 92.6025           & 88.0875          & 73.2875          & 80.6175           & 88.025         & 88.8725        &  &  &  &  &  \\
-  \textbf{Ethnicity (Percent)}        & Hispanic                                     & 19.53            & 17.8275         & 6.15              & 6.12             & 17.885           & 10.5              & 5.4475         & 11.6375        &  &  &  &  &  \\
-  \textbf{Education (Percent)}        & Associates                                   & 20.74            & 25              & 27.9225           & 26.46            & 24.4175          & 29.2675           & 26.315         & 30.9775        &  &  &  &  &  \\
-                            & Bachelor                                     & 26.53            & 21.4575         & 20.635            & 23.3325          & 18.785           & 18.3175           & 23.4075        & 14.595         &  &  &  &  &  \\
-                            & Graduate Degree                              & 21.14            & 16.475          & 14.6975           & 18.4525          & 16.3425          & 15.18             & 17.865         & 9.55           &  &  &  &  &  \\
-                            & HS Graduate                                  & 21.4725          & 26.7175         & 29.5875           & 26.0275          & 30.565           & 29.46             & 27.03          & 33.5125        &  &  &  &  &  \\
-                            & Less the High School                         & 10.12            & 10.3525         & 7.1575            & 5.7275           & 9.8875           & 7.7725            & 5.385          & 11.365         &  &  &  &  &  \\
-                            &                                              &                  &                 &                   &                  &                  &                   &                &                &  &  &  &  &
+  \begin{tabular}{lccccc}
+    \toprule
+    \textbf{Category} & \textbf{Fairfield County} & \textbf{Hartford County} & \textbf{Litchfield County} & \textbf{Middlesex County} \\
+    \midrule
+    Total Population & 944,977 & 894,465.25 & 182,657.5 & 163,318.25 \\
+    Race (Percent) & & & & \\
+    \quad American Indian and Alaska Native & 0.24 & 0.3075 & 0.2025 & 0.195 \\
+    \quad Asian & 5.2925 & 5.2925 & 1.9 & 3.0625 \\
+    \quad Black or African American & 11.405 & 13.7025 & 1.83 & 5.385 \\
+    \quad Native Hawaiian and Pacific Islander & 0.055 & 0.035 & 0 & 0.005 \\
+    \quad White & 72.6325 & 70.67 & 92.6025 & 88.0875 \\
+    Ethnicity (Percent) & & & & \\
+    \quad Hispanic & 19.53 & 17.8275 & 6.15 & 6.12 \\
+    \bottomrule
+  \end{tabular}%
+  }
+\end{table}
+
+\begin{table}[h]
+  \label{tab:Demographics}
+  \caption{Demographics and Education Levels for Counties 5-8}
+  \resizebox{\columnwidth}{!}{%
+  \begin{tabular}{lcccc}
+    \toprule
+    \textbf{Category} & \textbf{New Haven County} & \textbf{New London County} & \textbf{Tolland County} & \textbf{Windham County} \\
+    \midrule
+    Total Population & 858,678 & 268,477.75 & 151,218.75 & 116,608.75 \\
+    Race (Percent) & & & & \\
+    \quad American Indian and Alaska Native & 0.1725 & 0.605 & 0.05 & 0.565 \\
+    \quad Asian & 4.005 & 4.12 & 4.675 & 1.3675 \\
+    \quad Black or African American & 13.34 & 5.8175 & 3.1075 & 2.33 \\
+    \quad Native Hawaiian and Pacific Islander & 0.0225 & 0.025 & 0 & 0.015 \\
+    \quad White & 73.2875 & 80.6175 & 88.025 & 88.8725 \\
+    Ethnicity (Percent) & & & & \\
+    \quad Hispanic & 17.885 & 10.5 & 5.4475 & 11.6375 \\
+    \bottomrule
   \end{tabular}%
@@
 \begin{figure}[tbp]
+  \label{fig:Education by County Graph}
+    \centering
+    \includegraphics[width=\textwidth]{Education Levels by County.pdf}
+    \caption{Education Levels by County.}
+  \end{figure}
+
+\begin{figure}[tbp]
   \label{fig:Income by County Graph}
     \centering
-    \includegraphics[width=\textwidth]{Income by County Graph.pdf}
-    \caption{Median Income by County.}
+    \includegraphics[width=\textwidth]{Multiple Comparisons by County.pdf}
+    \caption{Social Needs Multiple Comparisons by County.}
   \end{figure}
+
+  \begin{table}[htbp]
+    \centering
+    \resizebox{\columnwidth}{!}{%
+    \begin{tabular}{lllrrrr}
+    \toprule
+    & & & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{2}{l}{95\% Confidence} \\
+    County 1(I) & County 2(J) & Mean Difference(I-J) & \multicolumn{1}{l}{Std. Error} & \multicolumn{1}{l}{Sig.} & \multicolumn{1}{l}{Lower Bound} & \multicolumn{1}{l}{Upper Bound} \\
+    \midrule
+    Fairfield County & Hartford County & 20565.50* & 1883.47 & \textbf{<.001} & 14327.60 & 26803.40 \\
+    & Litchfield County & 14919.50* & 1883.47 & \textbf{<.001} & 8681.60 & 21157.40 \\
+    & Middlesex County & 9671.75* & 1883.47 & \textbf{<.001} & 3433.85 & 15909.65 \\
+    & New Haven County & 25662.75* & 1883.47 & \textbf{<.001} & 19424.85 & 31900.65 \\
+    & New London County & 21456.50* & 1883.47 & \textbf{<.001} & 15218.60 & 27694.40 \\
+    & Tolland County & 8705.00* & 1883.47 & \textbf{0.002} & 2467.10 & 14942.90 \\
+    & Windham County & 28671.00* & 1883.47 & \textbf{<.001} & 22433.10 & 34908.90 \\
+    \midrule
+    Hartford County & Fairfield County & -20565.50* & 1883.47 & \textbf{<.001} & -26803.40 & -14327.60 \\
+    & Litchfield County & -5646 & 1883.47 & 0.096 & -11883.90 & 591.90 \\
+    & Middlesex County & -10893.75* & 1883.47 & \textbf{<.001} & -17131.65 & -4655.85 \\
+    & New Haven County & 5097.25 & 1883.47 & 0.169 & -1140.65 & 11335.15 \\
+    & New London County & 891 & 1883.47 & 1 & -5346.90 & 7128.90 \\
+    & Tolland County & -11860.50* & 1883.47 & \textbf{<.001} & -18098.40 & -5622.60 \\
+    & Windham County & 8105.50* & 1883.47 & \textbf{0.005} & 1867.60 & 14343.40 \\
+    \midrule
+    Litchfield County & Fairfield County & -14919.50* & 1883.47 & \textbf{<.001} & -21157.40 & -8681.60 \\
+    & Hartford County & 5646 & 1883.47 & 0.096 & -591.90 & 11883.90 \\
+    & Middlesex County & -5247.75 & 1883.47 & 0.145 & -11485.65 & 990.15 \\
+    & New Haven County & 10743.25* & 1883.47 & \textbf{<.001} & 4505.35 & 16981.15 \\
+    & New London County & 6537 & 1883.47 & 0.035 & 299.10 & 12774.90 \\
+    & Tolland County & -6214.5 & 1883.47 & 0.051 & -12452.40 & 23.40 \\
+    & Windham County & 13751.50* & 1883.47 & \textbf{<.001} & 7513.60 & 19989.40 \\
+    \midrule
+    Middlesex County & Fairfield County & -9671.75* & 1883.47 & \textbf{<.001} & -15909.65 & -3433.85 \\
+    & Hartford County & 10893.75* & 1883.47 & \textbf{<.001} & 4655.85 & 17131.65 \\
+    & Litchfield County & 5247.75 & 1883.47 & 0.145 & -990.15 & 11485.65 \\
+    & New Haven County & 15991.00* & 1883.47 & \textbf{<.001} & 9753.10 & 22228.90 \\
+    & New London County & 11784.75* & 1883.47 & \textbf{<.001} & 5546.85 & 18022.65 \\
+    & Tolland County & -966.75 & 1883.47 & 0.999 & -7204.65 & 5271.15 \\
+    & Windham County & 18999.25* & 1883.47 & \textbf{<.001} & 12761.35 & 25237.15 \\
+    \bottomrule
+  \end{tabular}%
+  }
+\end{table}
 

### 2023-12-15 manuscript/manuscript.tex
added multiple comparison by year and town graphs

--- 2023-12-15 manuscript/manuscript.tex
@@
 \usepackage{adjustbox}
+\usepackage[utf8]{inputenc}
 
@@
 
-\ref{tab:Demographics}
-\ref{fig:Income by County Graph}
+\ref{tab:Demographics1}
+\ref{tab:Demographics2}
+
+\ref{fig:Education by County Graph}
+discuss, use lit to support why
+
+\ref{fig:Social Needs by County Graph}
+differences by year
+
+\ref{tab:Multiple Comparison for Income}
+the specific values for income
+
+\ref{tab: Multiple Comparisons}
+what discussion talks about
 
 \begin{table}[h]
-\label{tab:Demographics}
+\label{tab:Demographics1}
   \caption{Demographics and Education Levels for Counties 1-4}
@@
     \quad Hispanic & 19.53 & 17.8275 & 6.15 & 6.12 \\
-    Education (Percent) & & & & \\
-    \quad Associates & 20.74 & 25 & 27.9225 & 26.46 \\
-    \quad Bachelor & 26.53 & 21.4575 & 20.635 & 23.3325 \\
-    \quad Graduate Degree & 21.14 & 16.475 & 14.6975 & 18.4525 \\
-    \quad HS Graduate & 21.4725 & 26.7175 & 29.5875 & 26.0275 \\
-    \quad Less than High School & 10.12 & 10.3525 & 7.1575 & 5.7275 \\
     \bottomrule
@@
 \begin{table}[h]
-  \label{tab:Demographics}
+  \label{tab:Demographics2}
   \caption{Demographics and Education Levels for Counties 5-8}
@@
     \quad Hispanic & 17.885 & 10.5 & 5.4475 & 11.6375 \\
-    Education (Percent) & & & & \\
-    \quad Associates & 24.4175 & 29.2675 & 26.315 & 30.9775 \\
-    \quad Bachelor & 18.785 & 18.3175 & 23.4075 & 14.595 \\
-    \quad Graduate Degree & 16.3425 & 15.18 & 17.865 & 9.55 \\
-    \quad HS Graduate & 30.565 & 29.46 & 27.03 & 33.5125 \\
-    \quad Less than High School & 9.8875 & 7.7725 & 5.385 & 11.365 \\
     \bottomrule
@@
 \begin{figure}[tbp]
-  \label{fig:Income by County Graph}
+  \label{fig:Education by County Graph}
     \centering
-    \includegraphics[width=\textwidth]{Income by County Graph.pdf}
-    \caption{Median Income by County.}
+    \includegraphics[width=\textwidth]{Education Levels by County.pdf}
+    \caption{Education Levels by County.}
+  \end{figure}
+
+\begin{figure}[tbp]
+  \label{fig:Social Needs by County Graph}
+    \centering
+    \includegraphics[width=\textwidth]{Multiple Comparisons by County.pdf}
+    \caption{Social Needs Multiple Comparisons by County.}
   \end{figure}
@@
   \begin{table}[htbp]
+    \label{tab:Multiple Comparison for Income}
+    \caption{Median Income Multiple Comparison by County}
     \centering
@@
     \midrule
-  Fairfield County & Hartford County & 20565.50000* & 1883.47243 & \textbf{<.001} & 14327.6034 & 26803.3966 \\
-  & Litchfield County & 14919.50000* & 1883.47243 & \textbf{<.001} & 8681.6034 & 21157.3966 \\
-  & Middlesex County & 9671.75000* & 1883.47243 & \textbf{<.001} & 3433.8534 & 15909.6466 \\
-  & New Haven County & 25662.75000* & 1883.47243 & \textbf{<.001} & 19424.8534 & 31900.6466 \\
-  & New London County & 21456.50000* & 1883.47243 & \textbf{<.001} & 15218.6034 & 27694.3966 \\
-  & Tolland County & 8705.00000* & 1883.47243 & \textbf{0.002} & 2467.1034 & 14942.8966 \\
-  & Windham County & 28671.00000* & 1883.47243 & \textbf{<.001} & 22433.1034 & 34908.8966 \\
+    Fairfield County & Hartford County & 20565.50* & 1883.47 & \textbf{\textless 0.001} & 14327.60 & 26803.40 \\
+    & Litchfield County & 14919.50* & 1883.47 & \textbf{\textless 0.001} & 8681.60 & 21157.40 \\
+    & Middlesex County & 9671.75* & 1883.47 & \textbf{<.001} & 3433.85 & 15909.65 \\
+    & New Haven County & 25662.75* & 1883.47 & \textbf{<.001} & 19424.85 & 31900.65 \\
+    & New London County & 21456.50* & 1883.47 & \textbf{<.001} & 15218.60 & 27694.40 \\
+    & Tolland County & 8705.00* & 1883.47 & \textbf{0.002} & 2467.10 & 14942.90 \\
+    & Windham County & 28671.00* & 1883.47 & \textbf{<.001} & 22433.10 & 34908.90 \\
     \midrule
@@
     & Tolland County & -11860.50* & 1883.47 & \textbf{<.001} & -18098.40 & -5622.60 \\
-  & Windham County & 8105.50* & 1883.47 & 0.005 & 1867.60 & 14343.40 \\
+    & Windham County & 8105.50* & 1883.47 & \textbf{0.005} & 1867.60 & 14343.40 \\
     \midrule
@@
     \midrule
-  Middlesex County & Fairfield County & -9671.75* &  & 1883.47 & <.001 & -15909.65 & -3433.85 \\
-  & Hartford County & 10893.75* & 1883.47 & <.001 & 4655.85 & 17131.65 \\
+    Middlesex County & Fairfield County & -9671.75* & 1883.47 & \textbf{<.001} & -15909.65 & -3433.85 \\
+    & Hartford County & 10893.75* & 1883.47 & \textbf{<.001} & 4655.85 & 17131.65 \\
     & Litchfield County & 5247.75 & 1883.47 & 0.145 & -990.15 & 11485.65 \\
-  & New Haven County & 15991.00* & 1883.47 & <.001 & 9753.10 & 22228.90 \\
-  & New London County & 11784.75* & 1883.47 & <.001 & 5546.85 & 18022.65 \\
+    & New Haven County & 15991.00* & 1883.47 & \textbf{<.001} & 9753.10 & 22228.90 \\
+    & New London County & 11784.75* & 1883.47 & \textbf{<.001} & 5546.85 & 18022.65 \\
     & Tolland County & -966.75 & 1883.47 & 0.999 & -7204.65 & 5271.15 \\
-  & Windham County & 18999.25* & 1883.47 & <.001 & 12761.35 & 25237.15 \\
+    & Windham County & 18999.25* & 1883.47 & \textbf{<.001} & 12761.35 & 25237.15 \\
     \midrule
-  New Haven County & Fairfield County & -25662.75* &  & 1883.47 & <.001 & -31900.65 & -19424.85 \\
+    New Haven County & Fairfield County & -25662.75* & 1883.47 & <.001 & -31900.65 & -19424.85 \\
     & Hartford County & -5097.25 & 1883.47 & 0.169 & -11335.15 & 1140.65 \\
@@
     & Tolland County & -16957.75* & 1883.47 & <.001 & -23195.65 & -10719.85 \\
-  & Windham County & 3008.25 & 1883.47 & 0.747 & -3229.65 & 9246
+    & Windham County & 3008.25 & 1883.47 & 0.747 & -3229.65 & 9246 \\
     \midrule
@@
     \midrule
-  Windham County & Fairfield County & -28671.00* &  & 1883.47 & <.001 & -34908.90 & -22433.10 \\
+    Windham County & Fairfield County & -28671.00* & 1883.47 & <.001 & -34908.90 & -22433.10 \\
     & Hartford County & -8105.50* & 1883.47 & 0.005 & -14343.40 & -1867.60 \\
@@
     & Tolland County & -19966.00* & 1883.47 & <.001 & -26203.90 & -13728.10 \\
+    \bottomrule
+  \end{tabular}%
+  }
+\end{table}
+
+\begin{table}[]
+  \label{tab: Multiple Comparisons}
+  \caption{Multiple Comparisons by Year and Town}
+  \resizebox{\columnwidth}{!}{%
+  \begin{tabular}{llrrrrl}
+  \textbf{Social Need}   & \textbf{Comparison by} & \multicolumn{1}{l}{\textbf{DF}} & \multicolumn{1}{l}{\textbf{Sum of Squares}} & \multicolumn{1}{l}{\textbf{Mean Square}} & \multicolumn{1}{l}{\textbf{F Value}} & \textbf{P Value}           \\
+  Median Income          & Year                   & 3                               & 158657606                                   & 52885869                                 & 95.57                                & <.0001                     \\
+                         & Town                   & 7                               & 2618521106                                  & 374074444                                & 675.99                               & <.0001                     \\
+  Food                   & Year                   & 3                               & 3.6450625                                   & 1.2150208                                & 10.08                                & 0.0003 \\
+                         & Town                   & 7                               & 348.3382875                                 & 49.7626125                               & 412.72                               & <.0001                     \\
+  Housing                & Year                   & 3                               & 1.4535125                                   & 0.4845042                                & 0.41                                 & 0.7506 \\
+                         & Town                   & 7                               & 183.9498375                                 & 26.2785482                               & 21.99                                & <.0001                     \\
+  Rehospitalization Rate & Year                   & 3                               & 0.00050938                                  & 0.00016979                               & 1.45                                 & 0.2578 \\
+                         & Town                   & 7                               & 0.00427188                                  & 0.00061027                               & 5.2                                  & 0.0015 \\
+  Uninsured Rate         & Year                   & 3                               & 2.6848375                                   & 0.89494583                               & 17.17                                & <.0001                     \\
+                         & Town                   & 7                               & 92.8554875                                  & 13.26506964                              & 254.57                               & <.0001
   \end{tabular}%
@@
 noticeable in counties 1 and 5, indicating enduring economic pressure.
+
+The results pertaining to housing defined by renters whose rent is 50 percent of their income, 
+reveal noteworthy patterns with respect to social needs. Examining the data across the four-year span 
+indicates a consistent trend, as no significant differences were observed. However, significant differences are 
+revealed when comparing between counties. Counties 1 and 5 exhibited a statistically significant increase 
+in the percentage of renters facing housing costs amounting to 50 percent of their income compared to 
+counties 2, 7, and 3. Intriguingly, there was no statistically significant distinction between counties 
+1 and 5, suggesting a commonality in the challenges faced by renters in these specific regions. These 
+findings underscore the importance of localized interventions and policy considerations to address the 
+distinct socio-economic dynamics influencing housing affordability across different counties.
+
+Food access was assesses through investigating the proportion of the population involved in the use of Food Stamps programs.
+AHRQ data reveals notable variations across different counties. Counties 8, 2, and 5 exhibit a statistically significant 
+higher percentage of the population relying on Food Stamps, suggesting a potentially elevated level of economic 
+vulnerability or socio-economic challenges in these areas. County 6 also demonstrates a substantial proportion 
+of its population on Food Stamps, indicating a notable need for social assistance. Conversely, County 7 stands 
+out with the lowest percentage of its population depending on Food Stamps, implying comparatively better 
+economic conditions or potentially more effective social support systems. These findings underscore the 
+importance of targeted interventions and resource allocation to address social needs, particularly in counties 
+with higher reliance on Food Stamps. Further exploration into the underlying factors contributing to these variations 
+is needed for informed policy development and community-specific interventions.
 

### 2023-12-15 manuscript/manuscript.tex
added descriptions of social need variables in introduction

@@
 \usepackage{adjustbox}
-\usepackage[utf8]{inputenc}
+\usepackage{booktabs}
+\usepackage{multirow}
+\usepackage{threeparttable}
 
@@
 \section{Introduction}\label{sec:intro}
-
+\\
+I. Prevalence of Social Determinants of Health 
+\\
 Current research focuses on how social determinants of health (SDoH) plays a  massive
@@
 these determinants within diverse communities. This research aims to bridge this gap by comprehensively assessing how 
-the pandemic has influenced key social determinants of health across various counties and racial groups in Connecticut. 
+the pandemic has influenced key social determinants of health across the 8 CT counties and a four year timeframe prior to 
+the start of the COVID pandemic. 
 By identifying the specific ways in which different communities were affected, this study contributes valuable insights 
 for targeted interventions, policy-making, and the development of equitable healthcare strategies.
+\\
+II. Introduction to the Impact of Social Needs(specify for CT)
+\\
+This study will compare each of the following social needs by Year(2017-2020) and by 8 CT Counties: 
+Median Income,
+Educaation,
+Food Access
+Housing Stability,
+Health Insurance,
+Reshospitalization rates.
+
+Income is a fundamental
+social need that significantly influences
+one's health. The level of income
+directly affects an individual's access
+to essential resources such as nutritious
+food, healthcare, and secure housing.
+People with lower incomes often face
+barriers to healthcare services and
+struggle to afford a balanced diet,
+leading to higher risks of chronic
+illnesses. Income disparities contribute
+to inequalities in health outcomes, as
+those with limited financial resources
+may experience higher stress levels and
+reduced access to preventive care.
+Addressing income inequality is crucial
+for promoting overall well-being and
+reducing health disparities in communities.
+
+Education is a key social determinant
+of health, influencing various aspects
+of an individual's life. Higher levels
+of education are associated with better
+health outcomes, as education enhances
+one's ability to make informed decisions
+about lifestyle choices, healthcare
+utilization, and disease prevention.
+Limited educational opportunities can
+result in lower health literacy, reducing
+an individual's capacity to navigate
+complex healthcare systems and understand
+preventive measures. Educational
+disparities contribute to a cycle of
+poor health outcomes, as individuals
+with lower levels of education may face
+challenges in securing stable employment
+and accessing adequate healthcare
+resources. Addressing educational
+inequalities is essential for fostering
+a healthier and more equitable society.
+
+Access to nutritious and sufficient
+food is a critical social need that
+directly impacts health. Food insecurity,
+often linked to low income, can lead to
+malnutrition, obesity, and various health
+issues. Lack of access to fresh and
+healthy foods contributes to the prevalence
+of chronic conditions such as diabetes
+and cardiovascular diseases. Current
+issues related to food include disparities
+in food availability, affordability, and
+nutritional quality, disproportionately
+affecting marginalized communities.
+Addressing these issues involves promoting
+food equity, supporting local agriculture,
+and implementing policies that ensure
+everyone has access to nutritious food,
+ultimately improving overall public health.
+
+Housing plays a vital role in determining
+health outcomes. Inadequate or unstable
+housing conditions can lead to physical
+and mental health issues. Homelessness
+and substandard living conditions expose
+individuals to environmental hazards,
+increase stress levels, and contribute
+to the spread of infectious diseases.
+The current housing crisis in many regions
+exacerbates these issues, with rising
+costs and limited affordable housing
+options. Addressing housing as a social
+need involves implementing policies to
+ensure affordable housing, preventing
+homelessness, and improving living
+conditions to create a foundation for
+better health outcomes.
+
+Access to healthcare through insurance
+is a critical social need that significantly
+impacts health outcomes. Lack of health
+insurance can lead to delayed or forgone
+medical care, resulting in the progression
+of illnesses and poorer health.
+Disparities in insurance coverage contribute
+to inequalities in healthcare access and
+health outcomes. Current issues include
+the high costs of healthcare and the
+existence of uninsured or underinsured
+populations. Addressing these challenges
+involves expanding access to affordable
+health insurance, implementing healthcare
+reforms, and promoting policies that
+ensure comprehensive coverage for all
+individuals.
+
+Rehospitalization refers to the phenomenon
+where individuals experience repeated
+hospital admissions, often due to
+complications or inadequate follow-up care.
+High rates of rehospitalization indicate
+gaps in healthcare delivery and management,
+impacting both individual well-being and
+healthcare system efficiency. This social
+need is indicative of issues such as
+insufficient post-discharge support,
+medication management, and coordination
+of care. Repeated hospitalizations not
+only strain healthcare resources but also
+have significant implications for the
+individuals involved, leading to increased
+morbidity, reduced quality of life, and
+higher healthcare costs. Addressing
+rehospitalization requires improvements
+in transitional care, enhanced coordination
+among healthcare providers, and better
+support systems for patients, especially
+those with chronic conditions, to ensure
+a smoother recovery and reduce the burden
+on healthcare systems. Recognizing and
+addressing these factors can contribute
+to overall health improvement, prevent
+unnecessary healthcare utilization, and
+enhance the effectiveness of healthcare
+services.
 
@@
 
-- The data will be presented in Section \ref{sec:data}
+- The data will be presented in Section\ref{sec:data}
 
-- The methods are described in Section \ref{sec:meth}
+- The methods are described in Section\ref{sec:meth}
 
-- The results are reported in Section \ref{sec:resu}
+- The results are reported in Section\ref{sec:resu}
 
-- A discussion concludes in Section \ref{sec:disc}
+- A discussion concludes in Section ref{sec:disc}
 
@@
 In this study, descriptive statistics is utilized to outline the total population, racial composition, 
-education levels, and average rehospitalization rate across the 8 counties in Connecticut. Chi-squared analyses were 
-conducted to assess the significance of the difference of the variables of median income, poverty level, health insurance, 
-utilities access, and electronics access between counties and across the four years. Additional 
+and education levels across the 8 counties in Connecticut. ANOVA analyses were 
+conducted to assess the significance of the difference of the variables of median income, health insurance, food access, housing, and rehospitalization rates between counties and across the four years.
+Additional
 Tukey's HSD tests were conducted to determine the specific counties and years that have had significant differences within 
@@
 
+County names are assigned to a respective county number: 
+1	Fairfield County,
+2	Hartford County,
+3	Litchfield County,
+4	Middlesex County,
+5	New Haven County,
+6	New London County,
+7	Tolland County,
+8	Windham County.
+
+The racial and ethnic distribution of the population of the 8 counties investigated in this study is displayed in the following graphs:
 \ref{tab:Demographics1}
 \ref{tab:Demographics2}
-
-\ref{fig:Education by County Graph}
-discuss, use lit to support why
-
-\ref{fig:Social Needs by County Graph}
-differences by year
-
-\ref{tab:Multiple Comparison for Income}
-the specific values for income
-
-\ref{tab: Multiple Comparisons}
-what discussion talks about
 
@@
 
+  \begin{figure}[tbp]
+    \label{fig:Social Needs by YearGraph}
+      \centering
+      \includegraphics[width=\textwidth]{By Year.pdf}
+      \caption{Social Needs Multiple Comparisons by County.}
+    \end{figure}
+
   \begin{table}[htbp]
@@
     \midrule
-    Fairfield County & Hartford County & 20565.50* & 1883.47 & \textbf{\textless 0.001} & 14327.60 & 26803.40 \\
-    & Litchfield County & 14919.50* & 1883.47 & \textbf{\textless 0.001} & 8681.60 & 21157.40 \\
-    & Middlesex County & 9671.75* & 1883.47 & \textbf{<.001} & 3433.85 & 15909.65 \\
-    & New Haven County & 25662.75* & 1883.47 & \textbf{<.001} & 19424.85 & 31900.65 \\
-    & New London County & 21456.50* & 1883.47 & \textbf{<.001} & 15218.60 & 27694.40 \\
+    Fairfield County & Hartford County & 20565.50* & 1883.47 & \textbf{\textless0.001} & 14327.60 & 26803.40 \\
+    & Litchfield County & 14919.50* & 1883.47 & \textbf{\textless0.001} & 8681.60 & 21157.40 \\
+    & Middlesex County & 9671.75* & 1883.47 & \textbf{\textless0.001} & 3433.85 & 15909.65 \\
+    & New Haven County & 25662.75* & 1883.47 & \textbf{\textless0.001} & 19424.85 & 31900.65 \\
+    & New London County & 21456.50* & 1883.47 & \textbf{\textless0.001} & 15218.60 & 27694.40 \\
     & Tolland County & 8705.00* & 1883.47 & \textbf{0.002} & 2467.10 & 14942.90 \\
-    & Windham County & 28671.00* & 1883.47 & \textbf{<.001} & 22433.10 & 34908.90 \\
+    & Windham County & 28671.00* & 1883.47 & \textbf{\textless0.001} & 22433.10 & 34908.90 \\
     \midrule
-    Hartford County & Fairfield County & -20565.50* & 1883.47 & \textbf{<.001} & -26803.40 & -14327.60 \\
+    Hartford County & Fairfield County & -20565.50* & 1883.47 & \textbf{\textless0.001} & -26803.40 & -14327.60 \\
     & Litchfield County & -5646 & 1883.47 & 0.096 & -11883.90 & 591.90 \\
-    & Middlesex County & -10893.75* & 1883.47 & \textbf{<.001} & -17131.65 & -4655.85 \\
+    & Middlesex County & -10893.75* & 1883.47 & \textbf{\textless0.001} & -17131.65 & -4655.85 \\
     & New Haven County & 5097.25 & 1883.47 & 0.169 & -1140.65 & 11335.15 \\
     & New London County & 891 & 1883.47 & 1 & -5346.90 & 7128.90 \\
-    & Tolland County & -11860.50* & 1883.47 & \textbf{<.001} & -18098.40 & -5622.60 \\
+    & Tolland County & -11860.50* & 1883.47 & \textbf{\textless0.001} & -18098.40 & -5622.60 \\
     & Windham County & 8105.50* & 1883.47 & \textbf{0.005} & 1867.60 & 14343.40 \\
     \midrule
-    Litchfield County & Fairfield County & -14919.50* & 1883.47 & \textbf{<.001} & -21157.40 & -8681.60 \\
+    Litchfield County & Fairfield County & -14919.50* & 1883.47 & \textbf{\textless0.001} & -21157.40 & -8681.60 \\
     & Hartford County & 5646 & 1883.47 & 0.096 & -591.90 & 11883.90 \\
     & Middlesex County & -5247.75 & 1883.47 & 0.145 & -11485.65 & 990.15 \\
-    & New Haven County & 10743.25* & 1883.47 & \textbf{<.001} & 4505.35 & 16981.15 \\
+    & New Haven County & 10743.25* & 1883.47 & \textbf{\textless0.001} & 4505.35 & 16981.15 \\
     & New London County & 6537 & 1883.47 & 0.035 & 299.10 & 12774.90 \\
     & Tolland County & -6214.5 & 1883.47 & 0.051 & -12452.40 & 23.40 \\
-    & Windham County & 13751.50* & 1883.47 & \textbf{<.001} & 7513.60 & 19989.40 \\
+    & Windham County & 13751.50* & 1883.47 & \textbf{\textless0.001} & 7513.60 & 19989.40 \\
     \midrule
-    Middlesex County & Fairfield County & -9671.75* & 1883.47 & \textbf{<.001} & -15909.65 & -3433.85 \\
-    & Hartford County & 10893.75* & 1883.47 & \textbf{<.001} & 4655.85 & 17131.65 \\
+    Middlesex County & Fairfield County & -9671.75* & 1883.47 & \textbf{\textless0.001} & -15909.65 & -3433.85 \\
+    & Hartford County & 10893.75* & 1883.47 & \textbf{\textless0.001} & 4655.85 & 17131.65 \\
     & Litchfield County & 5247.75 & 1883.47 & 0.145 & -990.15 & 11485.65 \\
-    & New Haven County & 15991.00* & 1883.47 & \textbf{<.001} & 9753.10 & 22228.90 \\
-    & New London County & 11784.75* & 1883.47 & \textbf{<.001} & 5546.85 & 18022.65 \\
+    & New Haven County & 15991.00* & 1883.47 & \textbf{\textless0.001} & 9753.10 & 22228.90 \\
+    & New London County & 11784.75* & 1883.47 & \textbf{\textless0.001} & 5546.85 & 18022.65 \\
     & Tolland County & -966.75 & 1883.47 & 0.999 & -7204.65 & 5271.15 \\
-    & Windham County & 18999.25* & 1883.47 & \textbf{<.001} & 12761.35 & 25237.15 \\
+    & Windham County & 18999.25* & 1883.47 & \textbf{\textless0.001} & 12761.35 & 25237.15 \\
     \midrule
-    New Haven County & Fairfield County & -25662.75* & 1883.47 & <.001 & -31900.65 & -19424.85 \\
+    New Haven County & Fairfield County & -25662.75* & 1883.47 & \textbf{\textless0.001} & -31900.65 & -19424.85 \\
     & Hartford County & -5097.25 & 1883.47 & 0.169 & -11335.15 & 1140.65 \\
-    & Litchfield County & -10743.25* & 1883.47 & <.001 & -16981.15 & -4505.35 \\
-    & Middlesex County & -15991.00* & 1883.47 & <.001 & -22228.90 & -9753.10 \\
+    & Litchfield County & -10743.25* & 1883.47 & \textbf{\textless0.001} & -16981.15 & -4505.35 \\
+    & Middlesex County & -15991.00* & 1883.47 & \textbf{\textless0.001} & -22228.90 & -9753.10 \\
     & New London County & -4206.25 & 1883.47 & 0.368 & -10444.15 & 2031.65 \\
-    & Tolland County & -16957.75* & 1883.47 & <.001 & -23195.65 & -10719.85 \\
+    & Tolland County & -16957.75* & 1883.47 & \textbf{\textless0.001} & -23195.65 & -10719.85 \\
     & Windham County & 3008.25 & 1883.47 & 0.747 & -3229.65 & 9246 \\
     \midrule
-    New London County & Fairfield County & -21456.50* & 1883.47 & <.001 & -27694.40 & -15218.60 \\
+    New London County & Fairfield County & -21456.50* & 1883.47 & \textbf{\textless0.001} & -27694.40 & -15218.60 \\
     & Hartford County & -891 & 1883.47 & 1 & -7128.90 & 5346.90 \\
     & Litchfield County & -6537.00* & 1883.47 & 0.035 & -12774.90 & -299.10 \\
-    & Middlesex County & -11784.75* & 1883.47 & <.001 & -18022.65 & -5546.85 \\
+    & Middlesex County & -11784.75* & 1883.47 & \textbf{\textless0.001} & -18022.65 & -5546.85 \\
     & New Haven County & 4206.25 & 1883.47 & 0.368 & -2031.65 & 10444.15 \\
-    & Tolland County & -12751.50* & 1883.47 & <.001 & -18989.40 & -6513.60 \\
+    & Tolland County & -12751.50* & 1883.47 & \textbf{\textless0.001} & -18989.40 & -6513.60 \\
     & Windham County & 7214.50* & 1883.47 & 0.016 & 976.60 & 13452.40 \\
@@
     Tolland County & Fairfield County & -8705.00* & 1883.47 & 0.002 & -14942.90 & -2467.10 \\
-    & Hartford County & 11860.50* & 1883.47 & <.001 & 5622.60 & 18098.40 \\
+    & Hartford County & 11860.50* & 1883.47 & \textbf{\textless0.001} & 5622.60 & 18098.40 \\
     & Litchfield County & 6214.50 & 1883.47 & 0.051 & -23.40 & 12452.40 \\
     & Middlesex County & 966.75 & 1883.47 & 0.999 & -5271.15 & 7204.65 \\
-    & New Haven County & 16957.75* & 1883.47 & <.001 & 10719.85 & 23195.65 \\
-    & New London County & 12751.50* & 1883.47 & <.001 & 6513.60 & 18989.40 \\
-    & Windham County & 19966.00* & 1883.47 & <.001 & 13728.10 & 26203.90 \\
+    & New Haven County & 16957.75* & 1883.47 & \textbf{\textless0.001} & 10719.85 & 23195.65 \\
+    & New London County & 12751.50* & 1883.47 & \textbf{\textless0.001} & 6513.60 & 18989.40 \\
+    & Windham County & 19966.00* & 1883.47 & \textbf{\textless0.001} & 13728.10 & 26203.90 \\
     \midrule
@@
     & Hartford County & -8105.50* & 1883.47 & 0.005 & -14343.40 & -1867.60 \\
-    & Litchfield County & -13751.50* & 1883.47 & <.001 & -19989.40 & -7513.60 \\
-    & Middlesex County & -18999.25* & 1883.47 & <.001 & -25237.15 & -12761.35 \\
+    & Litchfield County & -13751.50* & 1883.47 & \textbf{\textless0.001} & -19989.40 & -7513.60 \\
+    & Middlesex County & -18999.25* & 1883.47 & \textbf{\textless0.001} & -25237.15 & -12761.35 \\
     & New Haven County & -3008.25 & 1883.47 & 0.747 & -9246.15 & 3229.65 \\
     & New London County & -7214.50* & 1883.47 & 0.016 & -13452.40 & -976.60 \\
-    & Tolland County & -19966.00* & 1883.47 & <.001 & -26203.90 & -13728.10 \\
+    & Tolland County & -19966.00* & 1883.47 & \textbf{\textless0.001} & -26203.90 & -13728.10 \\
     \bottomrule
+    * The mean difference is significant at the 0.05 level\\
   \end{tabular}%
@@
   \begin{tabular}{llrrrrl}
-  \textbf{Social Need}   & \textbf{Comparison by} & \multicolumn{1}{l}{\textbf{DF}} & \multicolumn{1}{l}{\textbf{Sum of Squares}} & \multicolumn{1}{l}{\textbf{Mean Square}} & \multicolumn{1}{l}{\textbf{F Value}} & \textbf{P Value}           \\
-  Median Income          & Year                   & 3                               & 158657606                                   & 52885869                                 & 95.57                                & <.0001                     \\
-                         & Town                   & 7                               & 2618521106                                  & 374074444                                & 675.99                               & <.0001                     \\
-  Food                   & Year                   & 3                               & 3.6450625                                   & 1.2150208                                & 10.08                                & 0.0003 \\
-                         & Town                   & 7                               & 348.3382875                                 & 49.7626125                               & 412.72                               & <.0001                     \\
+  \textbf{Social Need}   & \textbf{Comparison by} & \multicolumn{1}{l}{\textbf{DF}} & \multicolumn{1}{l}{\textbf{Sum of Squares}} & \multicolumn{1}{l}{\textbf{Mean Square}} & \multicolumn{1}{l}{\textbf{F Value}} & \textbf{p Value}           \\
+  Median Income          & Year                   & 3                               & 158657606                                   & 52885869                                 & 95.57                                & \textbf{\textless0.001}                    \\
+                         & Town                   & 7                               & 2618521106                                  & 374074444                                & 675.99                               & \textbf{\textless0.001}                      \\
+  Food                   & Year                   & 3                               & 3.6450625                                   & 1.2150208                                & 10.08                                & \textbf{0.0003} \\
+                         & Town                   & 7                               & 348.3382875                                 & 49.7626125                               & 412.72                               & \textbf{\textless0.001}                      \\
   Housing                & Year                   & 3                               & 1.4535125                                   & 0.4845042                                & 0.41                                 & 0.7506 \\
-                         & Town                   & 7                               & 183.9498375                                 & 26.2785482                               & 21.99                                & <.0001                     \\
+                         & Town                   & 7                               & 183.9498375                                 & 26.2785482                               & 21.99                                & \textbf{\textless0.001}                      \\
   Rehospitalization Rate & Year                   & 3                               & 0.00050938                                  & 0.00016979                               & 1.45                                 & 0.2578 \\
-                         & Town                   & 7                               & 0.00427188                                  & 0.00061027                               & 5.2                                  & 0.0015 \\
-  Uninsured Rate         & Year                   & 3                               & 2.6848375                                   & 0.89494583                               & 17.17                                & <.0001                     \\
-                         & Town                   & 7                               & 92.8554875                                  & 13.26506964                              & 254.57                               & <.0001
+                         & Town                   & 7                               & 0.00427188                                  & 0.00061027                               & 5.2                                  & \textbf{0.0015} \\
+  Uninsured Rate         & Year                   & 3                               & 2.6848375                                   & 0.89494583                               & 17.17                                & \textbf{\textless0.001}                     \\
+                         & Town                   & 7                               & 92.8554875                                  & 13.26506964                              & 254.57                               & \textbf{\textless0.001}    \\
+  * The mean difference is significant at the 0.05 level\\
   \end{tabular}%
@@
 
-The results of the analysis shed light on the intricate relationships between county, race, and key 
-variables such as median income, housing affordability, rehospitalization rates, food stamps usage, 
-uninsured rates, and racial demographics. Understanding these correlations is vital in comprehending 
+\ref{fig:Education by County Graph}
+discuss, use lit to support why(descriptive) specific to CT
+
+Table 4\ref{fig:Social Needs by County Graph} reveals that there is a signifiant difference between 
+social need variables by year (2017-2020) for median income, food, and uninsured rate. Table 4 also 
+reveals that all five variables analyzes(median income, food, housing, rehospitalization rate, and 
+uninsured rate) are significantly difference. Multiple Comparison tests are conducted to identify the 
+specific similarities and differences between the 8 CT counties.
+\\
+I. Comparison by County
+\\
+The results of the Tukey multiple comparison analysis\ref{tab: Multiple Comparisons} shed light on the relationship between county and key 
+variables such as median income, housing affordability, rehospitalization rates, food stamps usage, and
+uninsured rates. Understanding these correlations is vital in comprehending 
 the socio-economic and racial disparities prevalent in the studied region.
@@
 compared to other counties, indicating potential disparities in resource access and opportunities. 
+\ref{tab:Multiple Comparison for Income} displays the individual significant levels for comparison with County 1.
+All counties 2-8 appear to be significantly different at p <0.05 compared to county 1.
 This wealth gap implies potential repercussions on community health outcomes. The consistent trend in 
@@
 
-The racial demographics highlight disparities in various counties. County 3's higher percentage of white 
-individuals, coupled with County 2, 5, and 1 having the highest black population, points to the need for
-targeted interventions addressing racial health inequalities. These disparities might be indicative of 
-historical, social, and economic factors influencing the healthcare experiences of different racial groups.
+These analyses reveals the presence of a drastic inequality in County 1(Fairfield County). Although Farfield County
+is revealed to have the highest median income, greatest educational attainment, Farfield County also has the greatest 
+percent population uninsured with health insurance and the greatest proportion of population whose renters pay rent 
+50 percent of their income. According to a study by the Federal Reserve Bank of New York{ ???????}, the most highest paid 
+workers in Fairfield County earn a salary that is nine times greater than their lower-wage counterparts. Technology causing the disparities
+\\
+II. Comparison by Year
+\\
+An analysis spanning four years indicates significant differences in median income, with the highest observed 
+in 2020 and the lowest in 2017. While there doesn't seem to be a notable overall difference in the proportion 
+of the population relying on food stamp programs or facing uninsured rates, distinctions emerge when considering 
+specific timeframes. The use of food stamps was higher in 2020 and 2019 compared to 2017, showcasing a 
+shift in reliance on such programs over the years. Similarly, the uninsured rates were notably higher in 2020 and 
+2018 compared to 2019. These findings suggest despite an overall increase in income over time, there is a simultaneous 
+growing demand for food stamp programs and a pressing need for improved access to affordable health insurance. 
+This suggests that, while income is on the rise, significant portions of the population still face challenges in
+ meeting basic needs and accessing essential services. Addressing these trends requires comprehensive strategies 
+ that go beyond income growth alone.
 

### 2023-12-15 manuscript/manuscript.tex
added analysis of education levels to discussion

@@
 \section{Introduction}\label{sec:intro}
-\\
+
 I. Prevalence of Social Determinants of Health
-\\
+
 Current research focuses on how social determinants of health (SDoH) plays a  massive
@@
 for targeted interventions, policy-making, and the development of equitable healthcare strategies.
-\\
+\@
 II. Introduction to the Impact of Social Needs(specify for CT)
@@
 Median Income,
-Educaation,
+Education,
 Food Access
@@
 reduced access to preventive care. 
+Data on income and mortality from the National Longitudinal Mortality Study reported by Backlund, Sorlie, and Johnson (1999) (4)
+reveals that a continued drop in mortality results as income increases with a more significant drop towards the lower portion of the distribution(4).
 Addressing income inequality is crucial
@@
 about lifestyle choices, healthcare
-utilization, and disease prevention.
+utilization, and disease prevention. In CT, it is revealed there has been a spike in chronic absenteeism during the onset of the pandemic.
+''Specifically, between the 2018-19 and 2021-22 school years, the share of students chronically absent grew by 13.5 percentage points.''(1)
+There is also evidence of decreased Connecticut Performance Index (CPI) below the state target levels from 2019 to 2022 in mathematics, science,
+and language arts.(1)
 Limited educational opportunities can
@@
 and accessing adequate healthcare
-resources. Addressing educational
-inequalities is essential for fostering
-a healthier and more equitable society.
+resources. COVID-19 has only exaggerated
+the pre-existing opportunity gap between urban schools and suburban schools in providing equal educational
+opportunities despite both being in Connecticut.(2)
+From (5), data reveals that  eath rates are lower for those with more education for all-cause mortality. 
+The gap between high school graduates and those with some post-secondary education are larger compared to the latter group consisting
+of a mixture of secondary education including college and advanced degrees.
 
-Access to nutritious and sufficient
+Access to sufficient
 food is a critical social need that
@@
 
+In Figure 1
 \ref{fig:Education by County Graph}
-discuss, use lit to support why(descriptive) specific to CT
+, clear distinctions among the eight counties are evident. 
+Specifically, Fairfield County stands out with the highest proportion of individuals attaining a bachelor's 
+degree as their highest level of education. Conversely, Windham County appears to lead in the percentage of 
+residents with a high school diploma as their highest educational attainment. These findings align with the median income 
+comparisons presented in Figure 2
+\ref{fig:Social Needs by County Graph}
+, covering the years 2017 to 2020. 
+During this period, Fairfield County consistently displayed the highest median income, while Windham County 
+consistently ranked lowest in terms of median income. This suggests a correlation between the counties with the 
+highest median income and those with a higher prevalence of individuals achieving higher levels of educational attainment.
 
-Table 4\ref{fig:Social Needs by County Graph} reveals that there is a signifiant difference between 
+Table 4
+\ref{fig:Social Needs by County Graph}
+ reveals that there is a significant difference between 
 social need variables by year (2017-2020) for median income, food, and uninsured rate. Table 4 also 
@@
 \\
-The results of the Tukey multiple comparison analysis\ref{tab: Multiple Comparisons} shed light on the relationship between county and key 
+The results of the Tukey multiple comparison analysis
+\ref{tab: Multiple Comparisons}
+ shed light on the relationship between county and key 
 variables such as median income, housing affordability, rehospitalization rates, food stamps usage, and
@@
 compared to other counties, indicating potential disparities in resource access and opportunities. 
-\ref{tab:Multiple Comparison for Income} displays the individual significant levels for comparison with County 1.
+\ref{tab:Multiple Comparison for Income}
+ displays the individual significant levels for comparison with County 1.
 All counties 2-8 appear to be significantly different at p <0.05 compared to county 1.
@@
 percent population uninsured with health insurance and the greatest proportion of population whose renters pay rent 
-50 percent of their income. According to a study by the Federal Reserve Bank of New York{ ???????}, the most highest paid 
+50 percent of their income. According to a study by the Federal Reserve Bank of New York{3}, the most highest paid 
 workers in Fairfield County earn a salary that is nine times greater than their lower-wage counterparts. Technology causing the disparities

### 2023-12-16 manuscript/manuscript.tex
replaced by year graph with new format

@@
 
-Income is a fundamental
-social need that significantly influences
-one's health. The level of income
+The level of income
 directly affects an individual's access
@@
 food, healthcare, and secure housing.
-People with lower incomes often face
+Those with lower incomes often face
 barriers to healthcare services and
@@
 
-Education is a key social determinant
-of health, influencing various aspects
-of an individual's life. Higher levels
+Higher levels
 of education are associated with better
@@
 
-Access to sufficient
-food is a critical social need that
-directly impacts health. Food insecurity,
+Food insecurity,
 often linked to low income, can lead to
@@
 affecting marginalized communities.
+In 2009, a nationwide analysis conducted by the USDA underscored the significance of both income inequality and racial segregation(6).
+The analysis indicated that in low-income areas, corner stores and similar establishments often provide 
+a surplus of processed foods with limited access to fresh items. However, healthier food options are 
+typically more prevalent in predominantly white communities compared to non-white communities.
 Addressing these issues involves promoting
@@
 to the spread of infectious diseases.
+Recent literature(8) has assessed the relationship between outcomes of health 
+and housing factors of physical health; mental health; chronic and infectious disease; maternal,
+ infant, reproductive, and sexual health; and injury. Studies have revealed that low income 
+ populations and those with high proportions of racial and ethnic minority groups face greater exposures to environmental hazards(8)
+Four pillars of housing has been used as a framework for assessing health-related aspects of 
+housing(7): 1) conditions (quality of housing); 2) cost (affordability); 3) consistency (residential stability); 
+and 4) context (neighborhood opportunities).
 The current housing crisis in many regions
@@
 of illnesses and poorer health. 
+Large disparities in health insurance coverage related to race and ethnicity remain a persisting issue of the US health care system
+further exacerbating health inequalities(9).
 Disparities in insurance coverage contribute
@@
 impacting both individual well-being and
-healthcare system efficiency. This social
+healthcare system efficiency(9).
+
+In 2011, around 3.3 million adults experienced hospital readmissions, 
+incurring associated costs amounting to approximately \$41.3 billion(10).
+
+This social
 need is indicative of issues such as
@@
 morbidity, reduced quality of life, and
-higher healthcare costs. Addressing
+higher healthcare costs(9). Addressing
 rehospitalization requires improvements
@@
 among healthcare providers, and better
-support systems for patients, especially
-those with chronic conditions, to ensure
-a smoother recovery and reduce the burden
-on healthcare systems. Recognizing and
+support systems for patients. Recognizing and
 addressing these factors can contribute
@@
 and education levels across the 8 counties in Connecticut. ANOVA analyses were 
-conducted to assess the significance of the difference of the variables of median income, health insurance, food access, housing, and rehospitalization rates between counties and across the four years.
-Additional
+conducted to assess the significance of the difference of the variables of median income, health insurance, food access, housing, 
+and rehospitalization rates between counties and across the four years using SAS v.9.4. Additional 
 Tukey's HSD tests were conducted to determine the specific counties and years that have had significant differences within 
-each of the variables for each county.
+each of the variables for each county using SAS v.9.4 and SPSS v.29.
 
@@
       \centering
-      \includegraphics[width=\textwidth]{By Year.pdf}
+      \includegraphics[width=\textwidth]{Social Need by Year.pdf}
       \caption{Social Needs Multiple Comparisons by County.}

### 2023-12-16 manuscript/manuscript.tex
added 10 references

@@
 
-Current research focuses on how social determinants of health (SDoH) plays a  massive
+Current research focuses on how social determinants of health (SDoH) play a massive
 impact on one's health; it is estimated that 80 percent of a population's health outcomes are 
-dictated by SDoH \citep{HOOD2016129}. Often, SDoH, when referring to an individual, can result in racial 
-disparities in care when looking at a population\citep{Monroe2023-uq}. It has been shown that major inefficiencies
+dictated by SDoH 
+\citep{HOOD2016129}
+. Often, SDoH, when referring to an individual, can result in racial 
+disparities in care when looking at a population
+\citep{Monroe2023-uq}
+. It has been shown that major inefficiencies
 in the health system are attributed to overlooked prevention opportunities and unequal access
-to care.\citep{Allin2014-xn}
+to care
+\citep{Allin2014-xn}.
 
-Understanding the intricate interplay of these social determinants is crucial in addressing health disparities 
+Understanding the interplay of these social determinants is crucial in addressing health disparities 
 and developing effective public health policies and interventions. The COVID-19 pandemic has shed new light on 
@@
 the pandemic has influenced key social determinants of health across the 8 CT counties and a four year timeframe prior to 
-the start of the COVID pandemic. 
-By identifying the specific ways in which different communities were affected, this study contributes valuable insights 
+the start of the COVID pandemic. By identifying the specific ways in which different communities were affected, this study contributes valuable insights 
 for targeted interventions, policy-making, and the development of equitable healthcare strategies.
-\@
-II. Introduction to the Impact of Social Needs(specify for CT)
-\\
+
+II. Introduction to the Impact of Social Needs
+
 This study will compare each of the following social needs by Year(2017-2020) and by 8 CT Counties: 
@@
 
-The level of income
+Level of income
 directly affects an individual's access
@@
 reduced access to preventive care. 
-Data on income and mortality from the National Longitudinal Mortality Study reported by Backlund, Sorlie, and Johnson (1999) (4)
-reveals that a continued drop in mortality results as income increases with a more significant drop towards the lower portion of the distribution(4).
+Data on income and mortality from 
+\citep{IOM2006}
+reveals that a continued drop in mortality results as income increases with a 
+more significant drop towards the lower portion of the distribution.
 Addressing income inequality is crucial
@@
 utilization, and disease prevention. In CT, it is revealed there has been a spike in chronic absenteeism during the onset of the pandemic.
-''Specifically, between the 2018-19 and 2021-22 school years, the share of students chronically absent grew by 13.5 percentage points.''(1)
+ ''Specifically, between the 2018-19 and 2021-22 school years, the share of students chronically absent grew by 13.5 percentage points.''\citep{CTGov}
 There is also evidence of decreased Connecticut Performance Index (CPI) below the state target levels from 2019 to 2022 in mathematics, science,
-and language arts.(1)
+and language arts
+\citep{CTGov}.
 Limited educational opportunities can
@@
 the pre-existing opportunity gap between urban schools and suburban schools in providing equal educational
-opportunities despite both being in Connecticut.(2)
-From (5), data reveals that  eath rates are lower for those with more education for all-cause mortality. 
+opportunities 
+\citep{MFoxCNBC_2020}.
+\citep{NCHS2004} reveals that death rates are lower for those with more education for all-cause mortality. 
 The gap between high school graduates and those with some post-secondary education are larger compared to the latter group consisting
@@
 affecting marginalized communities.
-In 2009, a nationwide analysis conducted by the USDA underscored the significance of both income inequality and racial segregation(6).
+In 2009, a nationwide analysis conducted by the USDA underscored the significance of both income inequality and racial segregation \citep{USDA_ERS2009}.
 The analysis indicated that in low-income areas, corner stores and similar establishments often provide 
@@
 individuals to environmental hazards,
-increase stress levels, and contribute
-to the spread of infectious diseases.
-Recent literature(8) has assessed the relationship between outcomes of health 
+increase stress levels, and contribute to the spread of infectious diseases.
+Recent literature \citep{Taylor2018} has assessed the relationship between outcomes of health 
 and housing factors of physical health; mental health; chronic and infectious disease; maternal,
  infant, reproductive, and sexual health; and injury. Studies have revealed that low income 
- populations and those with high proportions of racial and ethnic minority groups face greater exposures to environmental hazards(8)
+ populations and those with high proportions of racial and ethnic minority groups face greater exposures to environmental hazards 
+ \citep{Taylor2018}.
 Four pillars of housing has been used as a framework for assessing health-related aspects of 
-housing(7): 1) conditions (quality of housing); 2) cost (affordability); 3) consistency (residential stability); 
+housing \citep{Swope_Hernández_2019}: 1) conditions (quality of housing); 2) cost (affordability); 3) consistency (residential stability); 
 and 4) context (neighborhood opportunities).
@@
 of illnesses and poorer health. 
-Large disparities in health insurance coverage related to race and ethnicity remain a persisting issue of the US health care system
-further exacerbating health inequalities(9).
-Disparities in insurance coverage contribute
+Large disparities in health insurance coverage related to race and ethnicity remain a persistent issue within the US health care system
+and contribute
 to inequalities in healthcare access and
-health outcomes. Current issues include
-the high costs of healthcare and the
-existence of uninsured or underinsured
-populations. Addressing these challenges
+health outcomes 
+\citep{Buchmueller_Levinson_Levy_Wolfe_2016}.
+Addressing these challenges
 involves expanding access to affordable
@@
 impacting both individual well-being and
-healthcare system efficiency(9).
-
+healthcare system efficiency 
+\citep{Hudali2017}. 
 In 2011, around 3.3 million adults experienced hospital readmissions, 
-incurring associated costs amounting to approximately \$41.3 billion(10).
-
+incurring associated costs amounting to approximately \$41.3 billion 
+\citep{Hudali2017}.
 This social
@@
 morbidity, reduced quality of life, and
-higher healthcare costs(9). Addressing
+higher healthcare costs 
+\citep{Hudali2017}
+. Addressing
 rehospitalization requires improvements
@@
 
-- A discussion concludes in Section ref{sec:disc}
+- A discussion concludes in Section\ref{sec:disc}
 
@@
 Litchfield County, Middlesex County, New Haven County, New London County, Tolland County, Windham County) in Connecticut. These variables 
-encompass a total of 56 observations. The variables questions include housing, education level, income, insurance,
+encompass a total of 56 observations. The variables questions include housing affordability, education level, median income, health insurance,
 rehospitalization rates, food stamps usage, and population racial characteristics. The dataset includes a range of 
@@
 and education levels across the 8 counties in Connecticut. ANOVA analyses were 
-conducted to assess the significance of the difference of the variables of median income, health insurance, food access, housing, 
+conducted to assess the significance difference of the variables including median income, health insurance, food access, housing, 
 and rehospitalization rates between counties and across the four years using SAS v.9.4. Additional 
-Tukey's HSD tests were conducted to determine the specific counties and years that have had significant differences within 
-each of the variables for each county using SAS v.9.4 and SPSS v.29.
+Tukey's HSD tests were conducted to determine the significant impact of individual counties and years on
+each of the variables for each county and year using SAS v.9.4 and SPSS v.29.
 
@@
 8	Windham County.
+Years are assigned to a respective number: 
+1 2020,
+2 2019,
+3 2018,
+4 2017.
 
@@
 During this period, Fairfield County consistently displayed the highest median income, while Windham County 
-consistently ranked lowest in terms of median income. This suggests a correlation between the counties with the 
+consistently ranked lowest in terms of median income. This suggests a correlation between counties with
 highest median income and those with a higher prevalence of individuals achieving higher levels of educational attainment.
@@
 \ref{fig:Social Needs by County Graph}
- reveals that there is a significant difference between 
+ reveals a significant difference between 
 social need variables by year (2017-2020) for median income, food, and uninsured rate. Table 4 also 
 reveals that all five variables analyzes(median income, food, housing, rehospitalization rate, and 
-uninsured rate) are significantly difference. Multiple Comparison tests are conducted to identify the 
+uninsured rate) are significantly different. Multiple Comparison tests are conducted to identify the 
 specific similarities and differences between the 8 CT counties.
@@
 \ref{tab:Multiple Comparison for Income}
- displays the individual significant levels for comparison with County 1.
-All counties 2-8 appear to be significantly different at p <0.05 compared to county 1.
-This wealth gap implies potential repercussions on community health outcomes. The consistent trend in 
-the percentage of income spent on rent underscores a persistent challenge for residents, especially 
-noticeable in counties 1 and 5, indicating enduring economic pressure.
+ displays the individual significant levels of comparison with County 1.
+All counties 2-8 appear to be significantly different compared to county 1 with county 8 having the lowest median income.
 
@@
 indicates a consistent trend, as no significant differences were observed. However, significant differences are 
-revealed when comparing between counties. Counties 1 and 5 exhibited a statistically significant increase 
-in the percentage of renters facing housing costs amounting to 50 percent of their income compared to 
+revealed when comparing between counties. Counties 1 and 5 exhibited a statistically significant higher
+ percentage of renters facing housing costs amounting to 50 percent of their income compared to 
 counties 2, 7, and 3. Intriguingly, there was no statistically significant distinction between counties 
-1 and 5, suggesting a commonality in the challenges faced by renters in these specific regions. These 
+1 and 5. These 
 findings underscore the importance of localized interventions and policy considerations to address the 
@@
 vulnerability or socio-economic challenges in these areas. County 6 also demonstrates a substantial proportion 
-of its population on Food Stamps, indicating a notable need for social assistance. Conversely, County 7 stands 
+of its population on Food Stamps. Conversely, County 7 stands 
 out with the lowest percentage of its population depending on Food Stamps, implying comparatively better 
@@
 Rehospitalization rates demonstrate stability across counties and years leading up to 2020, suggesting 
-a consistent healthcare landscape. Counties 8, 2, and 5 exhibiting higher food stamp usage point to economic 
-challenges faced by residents in these regions. This trend aligns with housing affordability issues, 
-indicating a correlation between financial stress and reliance on government assistance programs.
+a consistent healthcare landscape. Figure 2 reveals that there is not a significant overall difference in rehospitalization rates between
+counties. However, Counties 1,5,6,2,3,8 appears to have the highest rehospitalization rates.
 
@@
 These analyses reveals the presence of a drastic inequality in County 1(Fairfield County). Although Farfield County
-is revealed to have the highest median income, greatest educational attainment, Farfield County also has the greatest 
+is revealed to have the highest median income, greatest educational attainment, Farfield County also maintains the greatest 
 percent population uninsured with health insurance and the greatest proportion of population whose renters pay rent 
-50 percent of their income. According to a study by the Federal Reserve Bank of New York{3}, the most highest paid 
-workers in Fairfield County earn a salary that is nine times greater than their lower-wage counterparts. Technology causing the disparities
+50 percent of their income. According to a study by the Federal Reserve Bank of New York 
+\citep{Liberty_Street_Economics_2021}, the most highest paid 
+workers in Fairfield County earn a salary that is nine times greater than their lower-wage counterparts. 
 \\
@@
 shift in reliance on such programs over the years. Similarly, the uninsured rates were notably higher in 2020 and 
-2018 compared to 2019. These findings suggest despite an overall increase in income over time, there is a simultaneous 
-growing demand for food stamp programs and a pressing need for improved access to affordable health insurance. 
-This suggests that, while income is on the rise, significant portions of the population still face challenges in
+2018 compared to 2019. These findings suggest despite an overall increase in income over time, there was a simultaneous 
+growing demand for food stamp programs and a pressing need for improved access to affordable health insurance leading up to the onset 
+of the COVID-19 pandemic. 
+This suggests that, while income is on the rise, significant portions of the population still faced challenges in
  meeting basic needs and accessing essential services. Addressing these trends requires comprehensive strategies 
@@
 
-\bibliography{../manuscript/ref}
+\bibliography{ref}
 \bibliographystyle{chicago}
@@
 \end{document}
-
-{housing by income.pdf}
-{housing by year.pdf}
-{Income by town.pdf}
-{Inome by year.pdf}
-{Rehosp by income/year.pdf}
-{Stamps by income/year.pdf}
